---
title: "descriptives"
format: html
---

```{r}
#| message: false
#| warning: false
filtered_data <- readRDS("../artifacts/filtered_data.rds")
codebook <- readRDS("../artifacts/codebook.rds")
source("../_common.R")
```

```{r}
#| message: false
#| warning: false
library(readr)
library(descr)
library(ggplot2)
library(purrr)
library(car)
library(janitor)
```

## ---- DESCRIPTIVES ----

## Identify variables

##### reasons_vars

```{r}
# Rationale for choices
reason_vars <- c(
  "REASONS_1", "REASONS_2", "REASONS_3", "REASONS_4",
  "REASONS_5", "REASONS_6", "REASONS_7", "REASONS_8",
  "reasons_comp_mean", "reasons_coop_mean", "reasons_combined_mean", "reasons_flip_mean"
)
```

##### manip_vars

```{r}
# # List of competition & cooperation variables, for reference
# comp_items_recoded <- c("RQ16.1_1","RQ16.1_2","RQ16.1_3","RQ16.1_4")
# comp_items_raw     <- c("Q16.1_1","Q16.1_2","Q16.1_3","Q16.1_4")
# coop_items_raw     <- c("Q16.1_5","Q16.1_6","Q16.1_7","Q16.1_8")

# state competition & cooperation
manip_vars <- c(
  "Manipulation_Coop_Mean",
  "Manipulation_Comp_Mean",
  "RManipulation_CoMp_Mean",
  "Manipulation_Mean"
)

# Manipulation_Mean calculated from SPSS
# COMPUTE Manipulation_Mean=MEAN(Manipulation_CooP_Mean,RManipulation_CoMp_Mean).
# VARIABLE LABELS  Manipulation_Mean 'Mean for cooperation and manipulation again'.
# EXECUTE.
```

##### sharing_vars

```{r}
# sharing from the task, sharing_vars
sharing_vars <- c(
  "public_more_shared",
  "public_less_shared",
  "private_more_shared",
  "private_less_shared"
)
```

##### NFC_vars

```{r}
# Need for cognition, NFC_vars
NFC_vars <- c(
  "NeedCog_Sum",
  "NeedCog_Mean"
)
```

##### SVO_vars

```{r}
# social value orientation, SVO_vars
SVO_vars <- c(
  "SVO_angle"
)
```

##### darktriad_vars

```{r}
# dark triad, darktriad_vars
darktriad_vars <- c(
  "DirtyDozen_Mean"
)
```

##### darktriad3_vars

```{r}
# dark triad, darktriad_vars
darktriad3_vars <- c(
  "DirtyDozen_Narcissism",
  "DirtyDozen_Psychopathy",
  "DirtyDozen_Machiavellianism"
)
```

## Participants

##### sex

1 = male; 2 = female.

```{r}
freq(as.ordered(filtered_data$Q14.2), plot = FALSE)
```

##### age

```{r}
mean(filtered_data$Q14.1, na.rm = TRUE)
sd(filtered_data$Q14.1, na.rm = TRUE)
```

The mean age of participants was X years old (SD = X). More women (X%) than men were in the sample. Approximately a quarter of the participants (X%) reported neither parent had attended college.

##### 🧇 Table: Freq table

```{r}
freq(as.ordered(filtered_data$Q14.2), plot = FALSE)
freq(as.ordered(filtered_data$Q14.3), plot = FALSE)
freq(as.ordered(filtered_data$hispanic), plot = FALSE)
freq(as.ordered(filtered_data$Race), plot = FALSE)
```

## Create and Run tables

##### reasons for choices

```{r}
reasoning_descriptives <- summarise_numeric(filtered_data, reason_vars)
reasoning_descriptives
```

##### state competition and cooperation

```{r}
manipulation_descriptives <- summarise_numeric(filtered_data, "Manipulation_Mean")
manipulation_descriptives
```

correlation between the two state sub-scales

```{r}
#correlation matrix

man_check_var <- c(
  "RQ16.1_1",
  "RQ16.1_2",
  "RQ16.1_3",
  "RQ16.1_4",
  "Q16.1_5",
  "Q16.1_6",
  "Q16.1_7",
  "Q16.1_8",
  "Manipulation_Coop_Mean",
  "Manipulation_Comp_Mean",
  "RManipulation_CoMp_Mean",
  "Manipulation_Mean"
)

corr_man_check <- corr_table(
  data = filtered_data,
  vars = man_check_var,
  labels = man_check_var,
  method = "spearman"
)

corr_man_check

write.csv(corr_man_check, "../tables/corr_man_check.csv", row.names = TRUE)
```

##### sharing for the task

```{r}
sharing_descriptives <- summarise_numeric(
  filtered_data, sharing_vars)
sharing_descriptives
```

##### need for cognition

```{r}
NFC_descriptives <- summarise_numeric(
  filtered_data, NFC_vars)
NFC_descriptives
```

##### social value orientation

```{r}
SVO_descriptives <- summarise_numeric(
  filtered_data, SVO_vars)
SVO_descriptives
```

##### dark triad

```{r}
darktriad_descriptives <- summarise_numeric(
  filtered_data, darktriad3_vars)
darktriad_descriptives
```

##### darktriad3

```{r}
darktriad3_descriptives <- summarise_numeric(
  filtered_data, darktriad3_vars)
darktriad3_descriptives
```

##### 🧇 Table: combine m and sd

```{r}
descriptives_all_data <- bind_rows(
  reasoning_descriptives,
  manipulation_descriptives,
  sharing_descriptives,
  NFC_descriptives,
  SVO_descriptives,
  darktriad_descriptives
  )

descriptives_all_data

write_csv(descriptives_all_data, "../tables/descriptives_all_data.csv")
```

## Outlier

```{r}

```

## Intercorrelations

Correlations among all variables that are included in the study.

##### 🧇 Table: correlation all

```{r}
# manipulations, items shared, competitiveness, then potential control variables
corr_all_vars <- c(
    "structure_number01",
    "motivation_number01",
    "public_more_shared",
    "public_less_shared",
    "private_more_shared",
    "private_less_shared",
    "Manipulation_Mean",
    "Q14.1",
    "sex",
    "SES_mean",
    "NeedCog_Mean",
    "DirtyDozen_Narcissism",
    "DirtyDozen_Psychopathy",
    "DirtyDozen_Machiavellianism",
    "SVO_angle"
  )
  
corr_all_label <- c(
    "Structure",
    "Motivation",
    "Common High",
    "Common Low",
    "Unique High",
    "Unique Low",
    "StateCompCoop",
    "Age",
    "Sex",
    "SES",
    "NFC",
    "Narcissism",
    "Psychopathy",
    "Machiavellianism",
    "SVO"
  )

corr_all_table <- corr_table(
  data = filtered_data,
  vars = corr_all_vars,
  labels = corr_all_label,
  method = "spearman"
)

corr_all_table

write_csv(corr_all_table, "../tables/corr_all_table.csv")
```

##### 🧇 Table: dark triad

```{r}
# manipulations, items shared, competitiveness, then potential control variables
corr_darktriad_vars <- c(
    "DirtyDozen_Narcissism",
    "DirtyDozen_Psychopathy",
    "DirtyDozen_Machiavellianism"
  )
  
corr_darktriad_label <- c(
    "Narcissism",
    "Psychopathy",
    "Machiavellianism"
  )

corr_darktriad_table <- corr_table(
  data = filtered_data,
  vars = corr_darktriad_vars,
  labels = corr_darktriad_label,
  method = "spearman"
)

corr_darktriad_table
```

dark core or dark personality traits, they are related moderately.

### Intentions to Share, Withhold, or Distort (making the case to merge withholding and distorting)

See the GEE model as the data is create there because new variables were created later in the document.

## Conditions comparisons

#### list controls

```{r}
# "structure_number01",  "motivation_number01",
controls <- c(
  "Q14.1",
  "sex",
  "SES_mean",   
  "hispanic",  # demographics / checks first
  "NeedCog_Mean",              # traits
  "DirtyDozen_Narcissism",
  "DirtyDozen_Psychopathy",
  "DirtyDozen_Machiavellianism",
  "SVO_angle"
)
```

#### descriptives

```{r}
desc_tbl <- map_dfr(controls, desc_by_cell)
desc_tbl
```

#### 🧇 Table: M (SD) of variables by condition

```{r}
# 1) say the order you want
var_order <- c(
  "Q14.1","sex","SES_mean", "hispanic",                # demographics / checks first
  "NeedCog_Mean",              # traits
  "DirtyDozen_Narcissism",
  "DirtyDozen_Psychopathy",
  "DirtyDozen_Machiavellianism",
  "SVO_angle"# or wherever you want it
)

cond_order <- c(                           # put the columns how you want them
  "individual–prosocial",
  "individual–proself",
  "group–prosocial",
  "group–proself"
)

# 2) prep, set factor levels for ordering, and pivot wide
apa_tbl <- desc_tbl %>%
  mutate(
    condition = paste(structure, motivation, sep = "–"),
    condition = factor(condition, levels = cond_order),
    variable  = factor(variable,  levels = var_order),
    cell      = sprintf("%.2f (%.2f)", M, SD)
  ) %>%
  dplyr::select(variable, condition, cell) %>%
  tidyr::pivot_wider(names_from = condition, values_from = cell) %>%
  arrange(variable) %>%                     # rows follow var_order
  dplyr::select(variable, any_of(cond_order))      # columns follow cond_order

apa_tbl
```

#### ANOVA results on controls

```{r}
## --- 4) Run across all control measures
anova_results <- set_names(lapply(controls, run_two_way_anova), controls)

# ## Example: Need for Cognition results
# anova_results$NeedCog_Mean$descriptives
# anova_results$NeedCog_Mean$anova_table
# anova_results$NeedCog_Mean$eta_sq
# anova_results$NeedCog_Mean$shapiro
# anova_results$NeedCog_Mean$levene

## --- 5) Combine outputs across all controls
anova_table_all <- imap_dfr(anova_results, ~ mutate(.x$anova_table, DV = .y))
anova_table_all

etas_all <- imap_dfr(anova_results, ~ mutate(.x$eta_sq, DV = .y))
etas_all
```

## END

```{r}
print("Success! All code has been run.")
```
