---
title: "03-01-06_InfoSharingBinomialLRT"
format: 
  html: {}
  pdf: {}
---

## setup ————————————————————————————

```{r}
#| warning: false
source("../_common.R")
```

### libraries

```{r}
library(openxlsx)
library(afex)
library(lme4)
library(emmeans)
library(papaja)

# library(glmmTMB)
# library(modelsummary)
# library(gtsummary)
# library(broom)
# library(DHARMa)

# library(RColorBrewer)
# library(tibble)
```

### read data

```{r}
dat_long <- read.xlsx("../artifacts/binominal_data.xlsx")
```

```{r}
sapply(
  dat_long %>%
    select(
      Q14.1,
      sex,
      SES_mean,
      hispanic,
      NeedCog_Mean,
      DirtyDozen_Narcissism,
      DirtyDozen_Psychopathy,
      DirtyDozen_Machiavellianism,
      SVO_angle
    ),
  class
)
```

```{r}
dat_long <- dat_long %>%
  mutate(
    DirtyDozen_Psychopathy = as.numeric(DirtyDozen_Psychopathy)
  )
```

### update data

Remove any cases which are missing. Causing warnings/issues with the model

```{r}
control_data <- dat_long %>%
  select(
    ItemResponse,
    InfoDistribution,
    InfoImportance,
    Q14.1,
    sex,
    SES_mean,
    hispanic,
    NeedCog_Mean,
    DirtyDozen_Narcissism,
    DirtyDozen_Psychopathy,
    DirtyDozen_Machiavellianism,
    SVO_angle,
    ResponseId,
    ItemID
  ) %>%
  drop_na() %>%
  droplevels()
```

Center variables to support model convergence

```{r}
control_data <- control_data %>%
  mutate(
    Age_z = as.numeric(scale(Q14.1)),
    SES_z = as.numeric(scale(SES_mean)),
    NFC_z = as.numeric(scale(NeedCog_Mean)),
    Narcissism_z = as.numeric(scale(DirtyDozen_Narcissism)),
    Psychopathy_z = as.numeric(scale(DirtyDozen_Psychopathy)),
    Machiavellianism_z = as.numeric(scale(DirtyDozen_Machiavellianism)),
    SVO_z = as.numeric(scale(SVO_angle))
  )
```

## control model ———————————————————————

```{r}
model_binom_lrt_controls <- mixed(
  ItemResponse ~
    InfoDistribution +
    InfoImportance +
    Age_z +
    sex +
    SES_z +
    hispanic +
    NFC_z +
    Narcissism_z +
    Psychopathy_z +
    Machiavellianism_z +
    SVO_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = control_data,
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)
```

```{r}
model_binom_lrt_controls
```

Only sex and NFC were significant

#### remove old data

```{r}
rm(control_data)
```

## full model —————————————————————————

#### create data

```{r}
full_model_data <- dat_long %>%
  select(
    ItemResponse,
    structure_number01,
    motivation_number01,
    InfoDistribution,
    InfoImportance,
    sex,
    NeedCog_Mean,
    ResponseId,
    ItemID
  ) %>%
  drop_na() %>%
  droplevels() %>%
  mutate(
    NeedCog_z = as.numeric(scale(NeedCog_Mean))
  )
```

#### model

Model includes optimization and centering of variables because of excessive warnings and failure to converge in previous attempts.

```{r}
model_binom_lrt <- mixed(
  ItemResponse ~
    structure_number01 *
    motivation_number01 *
    InfoDistribution *
    InfoImportance +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data,
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)
```

```{r}
model_binom_lrt
```

```{r}
anova(model_binom_lrt)
```

### four panel comparisons

#### high, common

```{r}
lrt_high_common <- mixed(
  ItemResponse ~
    structure_number01 * motivation_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "High Importance",
      InfoDistribution == "Common"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_high_common
```

#### high, unique

```{r}
lrt_high_unique <- mixed(
  ItemResponse ~
    structure_number01 * motivation_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "High Importance",
      InfoDistribution == "Unique"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_high_unique
```

#### low, common

```{r}
lrt_low_common <- mixed(
  ItemResponse ~
    structure_number01 * motivation_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "Low Importance",
      InfoDistribution == "Common"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_low_common
```

#### low, unique

```{r}
lrt_low_unique <- mixed(
  ItemResponse ~
    structure_number01 * motivation_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "Low Importance",
      InfoDistribution == "Unique"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_low_unique
```

### emmeans

estimation of sharing

#### emm

```{r}
lc_emm <- emmeans(
  lrt_low_common,
  ~ structure_number01 * motivation_number01,
  type = "response"
)

hc_emm <- emmeans(
  lrt_high_common,
  ~ structure_number01 * motivation_number01,
  type = "response"
)

lu_emm <- emmeans(
  lrt_low_unique,
  ~ structure_number01 * motivation_number01,
  type = "response"
)

hu_emm <- emmeans(
  lrt_high_unique,
  ~ structure_number01 * motivation_number01,
  type = "response"
)
```

```{r}
hc_structure <- emmeans(
  lrt_high_common,
  ~ structure_number01 | motivation_number01,
  type = "response"
)

hc_structure
# pairs(hc_structure, adjust = "holm")
```

```{r}
hc_motivation <- emmeans(
  lrt_high_common,
  ~ motivation_number01 | structure_number01,
  type = "response"
)

hc_motivation
# pairs(hc_motivation, adjust = "holm")
```

#### high, unique

```{r}
hu_structure <- emmeans(
  lrt_high_unique,
  ~ structure_number01,
  type = "response"
)

hu_structure
# pairs(hu_structure)
```

```{r}
hu_motivation <- emmeans(
  lrt_high_unique,
  ~ motivation_number01,
  type = "response"
)

hu_motivation
# pairs(hu_motivation)
```

### LRTs

#### high, common

##### structure among proself

Among Proself participants, does Interindividual differ from Intergroup?

```{r}
lrt_hc_structure_proself <- mixed(
  ItemResponse ~
    structure_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "High Importance",
      InfoDistribution == "Common",
      motivation_number01 == "Proself"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_hc_structure_proself
```

##### structure among prosocial

Among Prosocial participants, does Interindividual differ from Intergroup?

```{r}
lrt_hc_structure_prosocial <- mixed(
  ItemResponse ~
    structure_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "High Importance",
      InfoDistribution == "Common",
      motivation_number01 == "Prosocial"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_hc_structure_prosocial
```

##### motivation within interindividual

Within the Interindividual condition, do Proself and Prosocial participants differ?

```{r}
lrt_hc_motivation_interindividual <- mixed(
  ItemResponse ~
    motivation_number01 +
    sex +
    NeedCog_z +
    # (1 | ItemID) + # Item id removed because its estimated variance was 0, producting singular fit, bad model
    (1 | ResponseId), 
  data = full_model_data %>%
    filter(
      InfoImportance == "High Importance",
      InfoDistribution == "Common",
      structure_number01 == "Interindividual"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_hc_motivation_interindividual
```

There is only three items for each of the information types. The output below with Item ID included was showing that the model estimated variance among the items is zero. There was no detectable variation among the items.

```{r}
# VarCorr(lrt_hc_motivation_interindividual$full_model)
```

```{r}
# isSingular(lrt_hc_motivation_interindividual$full_model)
```

##### motivation within intergroup

Within the Intergroup condition, do Proself and Prosocial participants differ?

```{r}
lrt_hc_motivation_intergroup <- mixed(
  ItemResponse ~
    motivation_number01 +
    sex +
    NeedCog_z +
    (1 | ResponseId) +
    (1 | ItemID),
  data = full_model_data %>%
    filter(
      InfoImportance == "High Importance",
      InfoDistribution == "Common",
      structure_number01 == "Intergroup"
    ),
  family = binomial(link = "logit"),
  method = "LRT",
  control = glmerControl(
    optimizer = "bobyqa",
    optCtrl = list(maxfun = 200000)
  )
)

lrt_hc_motivation_intergroup
```

#### check

None of the other models had the issue with ID, so I will keep ID there. It is removed from only the one model because it was the failure point.

```{r}
VarCorr(lrt_hc_structure_proself$full_model)

VarCorr(lrt_hc_structure_prosocial$full_model)

VarCorr(lrt_hc_motivation_interindividual$full_model)

VarCorr(lrt_hc_motivation_intergroup$full_model)
```

#### high, unique

NA because there were only main effects, no interaction

## tables ——————————————————————————

### control variables

#### coef_table

```{r}
coef_table <- as.data.frame(
  summary(model_binom_lrt_controls$full_model)$coefficients
) %>%
  tibble::rownames_to_column("term") %>%
  mutate(
    OR = exp(Estimate),
    CI_low = exp(Estimate - 1.96 * `Std. Error`),
    CI_high = exp(Estimate + 1.96 * `Std. Error`)
  ) %>%
  select(
    term,
    Estimate,
    SE = `Std. Error`,
    OR,
    CI_low,
    CI_high
  )
```

#### lrt_table

```{r}
lrt_table <- as.data.frame(
  model_binom_lrt_controls$anova_table
) %>%
  tibble::rownames_to_column("effect") %>%
  transmute(
    effect,
    LR_Chisq = Chisq,
    p = `Pr(>Chisq)`
  )
```

#### name comparison

```{r}
coef_table$term
lrt_table$effect
```

#### term_map

```{r}
term_map <- tibble::tribble(
  ~term, ~effect, ~Predictor,

  "(Intercept)",
  NA_character_,
  "Intercept",

  "InfoDistribution1",
  "InfoDistribution",
  "Information Distribution",

  "InfoImportance1",
  "InfoImportance",
  "Information Importance",

  "Age_z",
  "Age_z",
  "Age",

  "sex",
  "sex",
  "Sex (1 = Female)",

  "SES_z",
  "SES_z",
  "Socioeconomic Status",

  "hispanic",
  "hispanic",
  "Hispanic",

  "NFC_z",
  "NFC_z",
  "Need for Cognition",

  "Narcissism_z",
  "Narcissism_z",
  "Narcissism",

  "Psychopathy_z",
  "Psychopathy_z",
  "Psychopathy",

  "Machiavellianism_z",
  "Machiavellianism_z",
  "Machiavellianism",

  "SVO_z",
  "SVO_z",
  "Social Value Orientation"
)
```

#### left join

```{r}
table_control_model <- term_map %>%
  left_join(coef_table, by = "term") %>%
  left_join(lrt_table, by = "effect")
```

#### table data

```{r}
table_control_model <- table_control_model %>%
  mutate(
    Estimate = sprintf("%.2f", Estimate),
    SE = sprintf("%.2f", SE),

    LR_Chisq = case_when(
      Predictor == "Intercept" ~ "—",
      is.na(LR_Chisq) ~ "",
      TRUE ~ sprintf("%.2f", LR_Chisq)
    ),

    p = case_when(
      Predictor == "Intercept" ~ "—",
      is.na(p) ~ "",
      p < .001 ~ "< .001",
      TRUE ~ sub("^0", "", sprintf("%.3f", p))
    ),

    OR_CI = sprintf(
      "%.2f [%.2f, %.2f]",
      OR,
      CI_low,
      CI_high
    )
  ) %>%
  select(
    Predictor,
    Estimate,
    SE,
    LR_Chisq,
    p,
    OR_CI
  )
```

```{r}
table_control_model <- bind_rows(
  table_control_model %>% slice(1),

  tibble(
    Predictor = "Item Characteristics",
    Estimate = "",
    SE = "",
    LR_Chisq = "",
    p = "",
    OR_CI = ""
  ),

  table_control_model %>% slice(2:3),

  tibble(
    Predictor = "Candidate Control Variables",
    Estimate = "",
    SE = "",
    LR_Chisq = "",
    p = "",
    OR_CI = ""
  ),

  table_control_model %>% slice(4:n())
)
```

```{r}
table_control_model
```

### full model

#### coef_table

```{r}
coef_table <- as.data.frame(
  summary(model_binom_lrt$full_model)$coefficients
) %>%
  tibble::rownames_to_column("term") %>%
  mutate(
    OR = exp(Estimate),
    CI_low = exp(Estimate - 1.96 * `Std. Error`),
    CI_high = exp(Estimate + 1.96 * `Std. Error`)
  ) %>%
  select(
    term,
    Estimate,
    SE = `Std. Error`,
    OR,
    CI_low,
    CI_high
  )
```

#### lrt_table

```{r}
lrt_table <- as.data.frame(
  model_binom_lrt$anova_table
) %>%
  tibble::rownames_to_column("effect") %>%
  transmute(
    effect,
    LR_Chisq = Chisq,
    p = `Pr(>Chisq)`
  )
```

#### name comparison

```{r}
coef_table$term
lrt_table$effect
```

#### term_map

```{r}
term_map <- tibble::tribble(
  ~term, ~effect, ~Predictor,

  "(Intercept)", NA_character_, "Intercept",

  "sex",
  "sex",
  "Sex (1 = Female)",

  "NeedCog_z",
  "NeedCog_z",
  "Need for Cognition",

  "structure_number011",
  "structure_number01",
  "Interindividual (0) vs. Intergroup (1)",

  "motivation_number011",
  "motivation_number01",
  "Proself (0) vs. Prosocial (1)",

  "InfoDistribution1",
  "InfoDistribution",
  "Common (0) vs. Unique (1)",

  "InfoImportance1",
  "InfoImportance",
  "Low (0) vs. High (1)",

  "structure_number011:motivation_number011",
  "structure_number01:motivation_number01",
  "Structure × Motivation",

  "structure_number011:InfoDistribution1",
  "structure_number01:InfoDistribution",
  "Structure × Distribution",

  "motivation_number011:InfoDistribution1",
  "motivation_number01:InfoDistribution",
  "Motivation × Distribution",

  "structure_number011:InfoImportance1",
  "structure_number01:InfoImportance",
  "Structure × Importance",

  "motivation_number011:InfoImportance1",
  "motivation_number01:InfoImportance",
  "Motivation × Importance",

  "InfoDistribution1:InfoImportance1",
  "InfoDistribution:InfoImportance",
  "Distribution × Importance",

  "structure_number011:motivation_number011:InfoDistribution1",
  "structure_number01:motivation_number01:InfoDistribution",
  "Structure × Motivation × Distribution",

  "structure_number011:motivation_number011:InfoImportance1",
  "structure_number01:motivation_number01:InfoImportance",
  "Structure × Motivation × Importance",

  "structure_number011:InfoDistribution1:InfoImportance1",
  "structure_number01:InfoDistribution:InfoImportance",
  "Structure × Distribution × Importance",

  "motivation_number011:InfoDistribution1:InfoImportance1",
  "motivation_number01:InfoDistribution:InfoImportance",
  "Motivation × Distribution × Importance",

  "structure_number011:motivation_number011:InfoDistribution1:InfoImportance1",
  "structure_number01:motivation_number01:InfoDistribution:InfoImportance",
  "Structure × Motivation × Distribution × Importance"
)
```

#### left join

```{r}
table_full_model <- term_map %>%
  left_join(coef_table, by = "term") %>%
  left_join(lrt_table, by = "effect")
```

#### table data

```{r}
table_full_model <- table_full_model %>%
  mutate(
    Estimate = sprintf("%.2f", Estimate),
    SE = sprintf("%.2f", SE),

    LR_Chisq = case_when(
      Predictor == "Intercept" ~ "—",
      is.na(LR_Chisq) ~ "",
      TRUE ~ sprintf("%.2f", LR_Chisq)
    ),

    p = case_when(
      Predictor == "Intercept" ~ "—",
      is.na(p) ~ "",
      p < .001 ~ "< .001",
      TRUE ~ sub("^0", "", sprintf("%.3f", p))
    ),

    OR_CI = sprintf(
      "%.2f [%.2f, %.2f]",
      OR,
      CI_low,
      CI_high
    )
  ) %>%
  select(
    Predictor,
    Estimate,
    SE,
    LR_Chisq,
    p,
    OR_CI
  )
```

```{r}
table_full_model <- bind_rows(
  table_full_model %>% slice(1),

  tibble(
    Predictor = "Control Variables",
    Estimate = "",
    SE = "",
    LR_Chisq = "",
    p = "",
    OR_CI = ""
  ),
  table_full_model %>% slice(2:3),

  tibble(
    Predictor = "Between Manipulations",
    Estimate = "",
    SE = "",
    LR_Chisq = "",
    p = "",
    OR_CI = ""
  ),
  table_full_model %>% slice(4:5),

  tibble(
    Predictor = "Within Manipulations",
    Estimate = "",
    SE = "",
    LR_Chisq = "",
    p = "",
    OR_CI = ""
  ),
  table_full_model %>% slice(6:7),

  tibble(
    Predictor = "Interactions",
    Estimate = "",
    SE = "",
    LR_Chisq = "",
    p = "",
    OR_CI = ""
  ),
  table_full_model %>% slice(8:n())
)
```

```{r}
table_full_model
rm(term_map)
```

### panels

```{r}
extract_panel <- function(model, clue_label) {

  as.data.frame(model$anova_table) %>%
    tibble::rownames_to_column("effect") %>%
    filter(
      effect %in% c(
        "structure_number01",
        "motivation_number01",
        "structure_number01:motivation_number01"
      )
    ) %>%
    transmute(
      Clue = clue_label,
      effect,
      LR_Chisq = Chisq,
      p = `Pr(>Chisq)`
    )
}
```

```{r}
panel_results <- bind_rows(
  extract_panel(lrt_high_common, "Common, High"),
  extract_panel(lrt_high_unique, "Unique, High"),
  extract_panel(lrt_low_common, "Common, Low"),
  extract_panel(lrt_low_unique, "Unique, Low")
)
```

```{r}
panel_results <- panel_results %>%
  mutate(
    result = paste0(
      format_stat(LR_Chisq),
      " (",
      format_stat(p, p_value = TRUE),
      ")"
    ),

    effect = recode(
      effect,
      "structure_number01" = "Structure",
      "motivation_number01" = "Motivation",
      "structure_number01:motivation_number01" =
        "Structure × Motivation"
    )
  )
```

#### table_panel

```{r}
table_panel <- panel_results %>%
  select(
    Clue,
    effect,
    result
  ) %>%
  tidyr::pivot_wider(
    names_from = effect,
    values_from = result
  )
```

```{r}
table_panel
rm(panel_results, extract_panel)
```

### estimated probabilities

#### dataframe

```{r}
probability_table_data <- bind_rows(
  as.data.frame(lc_emm) %>% mutate(Clue = "Common, Low"),
  as.data.frame(hc_emm) %>% mutate(Clue = "Common, High"),
  as.data.frame(lu_emm) %>% mutate(Clue = "Unique, Low"),
  as.data.frame(hu_emm) %>% mutate(Clue = "Unique, High")
) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    ),

    Condition = paste(
      structure_number01,
      motivation_number01,
      sep = ", "
    )
  )
```

```{r}
table_probability <- probability_table_data %>%
  select(
    Clue,
    Condition,
    P_CI
  ) %>%
  tidyr::pivot_wider(
    names_from = Condition,
    values_from = P_CI
  )
```

```{r}
table_probability <- table_probability %>%
  mutate(
    Clue = factor(
      Clue,
      levels = c(
        "Common, Low",
        "Common, High",
        "Unique, Low",
        "Unique, High"
      )
    )
  ) %>%
  arrange(Clue) %>%
  select(
    Clue,
    `Interindividual, Prosocial`,
    `Interindividual, Proself`,
    `Intergroup, Prosocial`,
    `Intergroup, Proself`
  )
```

```{r}
table_probability
```

### follow-up comparisons

#### dataframe

```{r}
hc_structure_or <- summary(
  pairs(
    hc_structure,
    reverse = TRUE,
    adjust = "none"
  ),
  type = "response",
  infer = c(TRUE, FALSE)
) %>%
  as.data.frame()

hc_motivation_or <- summary(
  pairs(
    hc_motivation,
    adjust = "none"
  ),
  type = "response",
  infer = c(TRUE, FALSE)
) %>%
  as.data.frame()

hu_structure_or <- summary(
  pairs(
    hu_structure,
    reverse = TRUE,
    adjust = "none"
  ),
  type = "response",
  infer = c(TRUE, FALSE)
) %>%
  as.data.frame()

hu_motivation_or <- summary(
  pairs(
    hu_motivation,
    adjust = "none"
  ),
  type = "response",
  infer = c(TRUE, FALSE)
) %>%
  as.data.frame()
```

```{r}
hc_lrt_p <- c(
  lrt_hc_structure_proself$anova_table[
    "structure_number01", "Pr(>Chisq)"
  ],

  lrt_hc_structure_prosocial$anova_table[
    "structure_number01", "Pr(>Chisq)"
  ],

  lrt_hc_motivation_interindividual$anova_table[
    "motivation_number01", "Pr(>Chisq)"
  ],

  lrt_hc_motivation_intergroup$anova_table[
    "motivation_number01", "Pr(>Chisq)"
  ]
)
```

```{r}
hc_lrt_p_holm <- p.adjust(
  hc_lrt_p,
  method = "holm"
) 
```

```{r}
hu_structure_p <- lrt_high_unique$anova_table[
  "structure_number01",
  "Pr(>Chisq)"
]

hu_motivation_p <- lrt_high_unique$anova_table[
  "motivation_number01",
  "Pr(>Chisq)"
]
```

```{r}
common_high_table <- tibble(
  Clue = c(
    "Common, High",
    "",
    "",
    ""
  ),

  Comparison = c(
    "Proself: Interindividual vs. Intergroup",
    "Prosocial: Interindividual vs. Intergroup",
    "Interindividual: Proself vs. Prosocial",
    "Intergroup: Proself vs. Prosocial"
  ),

  OR_CI = c(
    format_or_ci(
      hc_structure_or$odds.ratio[
        hc_structure_or$motivation_number01 == "Proself"
      ],
      hc_structure_or$asymp.LCL[
        hc_structure_or$motivation_number01 == "Proself"
      ],
      hc_structure_or$asymp.UCL[
        hc_structure_or$motivation_number01 == "Proself"
      ]
    ),

    format_or_ci(
      hc_structure_or$odds.ratio[
        hc_structure_or$motivation_number01 == "Prosocial"
      ],
      hc_structure_or$asymp.LCL[
        hc_structure_or$motivation_number01 == "Prosocial"
      ],
      hc_structure_or$asymp.UCL[
        hc_structure_or$motivation_number01 == "Prosocial"
      ]
    ),

    format_or_ci(
      hc_motivation_or$odds.ratio[
        hc_motivation_or$structure_number01 == "Interindividual"
      ],
      hc_motivation_or$asymp.LCL[
        hc_motivation_or$structure_number01 == "Interindividual"
      ],
      hc_motivation_or$asymp.UCL[
        hc_motivation_or$structure_number01 == "Interindividual"
      ]
    ),

    format_or_ci(
      hc_motivation_or$odds.ratio[
        hc_motivation_or$structure_number01 == "Intergroup"
      ],
      hc_motivation_or$asymp.LCL[
        hc_motivation_or$structure_number01 == "Intergroup"
      ],
      hc_motivation_or$asymp.UCL[
        hc_motivation_or$structure_number01 == "Intergroup"
      ]
    )
  ),

  p = format_stat(
    hc_lrt_p_holm,
    p_value = TRUE
  )
)
```

```{r}
unique_high_table <- tibble(
  Clue = c(
    "Unique, High",
    ""
  ),

  Comparison = c(
    "Interindividual vs. Intergroup",
    "Proself vs. Prosocial"
  ),

  OR_CI = c(
    format_or_ci(
      hu_structure_or$odds.ratio,
      hu_structure_or$asymp.LCL,
      hu_structure_or$asymp.UCL
    ),

    format_or_ci(
      hu_motivation_or$odds.ratio,
      hu_motivation_or$asymp.LCL,
      hu_motivation_or$asymp.UCL
    )
  ),

  p = c(
    format_stat(
      hu_structure_p,
      p_value = TRUE
    ),

    format_stat(
      hu_motivation_p,
      p_value = TRUE
    )
  )
)
```

```{r}
table_followup <- bind_rows(
  common_high_table,
  unique_high_table
)

table_followup
rm(unique_high_table, common_high_table, hu_motivation_p, hu_structure_p, hc_lrt_p_holm, hc_lrt_p)
```

## figures ———————————–——————————————-

```{r}
emm_sm_df <- bind_rows(
  as.data.frame(lc_emm) %>%
    mutate(
      InfoDistribution = "Common",
      InfoImportance = "Low"
    ),

  as.data.frame(hc_emm) %>%
    mutate(
      InfoDistribution = "Common",
      InfoImportance = "High"
    ),

  as.data.frame(lu_emm) %>%
    mutate(
      InfoDistribution = "Unique",
      InfoImportance = "Low"
    ),

  as.data.frame(hu_emm) %>%
    mutate(
      InfoDistribution = "Unique",
      InfoImportance = "High"
    )
) %>%
  mutate(
    structure_number01 = factor(
      structure_number01,
      levels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      motivation_number01,
      levels = c("Proself", "Prosocial")
    ),
    InfoDistribution = factor(
      InfoDistribution,
      levels = c("Common", "Unique")
    ),
    InfoImportance = factor(
      InfoImportance,
      levels = c("Low", "High")
    )
  )
```

```{r}
fig_emm_sm <- ggplot(
  emm_sm_df,
  aes(
    x = structure_number01,
    y = prob,
    fill = motivation_number01
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    alpha = 0.5,
    color = "black",
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL
    ),
    position = position_dodge(width = 0.8),
    width = 0.25,
    linewidth = 0.8
  ) +
  facet_grid(
    InfoDistribution ~ InfoImportance
  ) +
  scale_y_continuous(
    breaks = seq(0, 1, 0.2),
    limits = c(0, 1)
  ) +
  theme_apa() +
  theme(
    text = element_text(
      size = 12,
      family = "serif",
      color = "black"
    ),
    axis.title = element_text(
      size = 12,
      face = "plain",
      color = "black"
    ),
    axis.text = element_text(
      size = 11,
      face = "plain",
      color = "black"
    ),
    strip.text = element_text(
      size = 12,
      face = "plain",
      family = "serif"
    ),
    legend.title = element_text(
      size = 12,
      face = "plain"
    ),
    legend.text = element_text(
      size = 11,
      face = "plain"
    ),
    axis.ticks = element_line(
      color = "black",
      linewidth = 0.5
    ),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(
      color = "black"
    ),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(0.8, "lines")
  ) +
  labs(
    x = "Structure",
    y = "Predicted Probability of Sharing",
    fill = "Motivation"
  ) +
  scale_fill_manual(
    name = "Motivation",
    values = c(
      "Proself" = "#0C7BDC",
      "Prosocial" = "#FFC20A"
    )
  )

fig_emm_sm
```

## save ————————————————————————————

```{r}
# Create workbook to save the analyses
wb <- createWorkbook()
excel_export_file_location <- "../artifacts/binomialLRT_output.xlsx"

# Start fresh each time
if (file.exists(excel_export_file_location)) {
  file.remove(excel_export_file_location)
}
```

```{r}
save_output_to_workbook(
  wb, 
  sheet_name = "control model", 
  output = table_control_model
)

save_output_to_workbook(
  wb, 
  sheet_name = "full model", 
  output = table_full_model
)

save_figure_to_workbook(
  wb = wb,
  sheet_name = "Figure",
  figure_file = "../figures/EstProb.png",
  plot_obj = fig_emm_sm,
  width = 8,
  height = 6,
  dpi = 300
)

save_output_to_workbook(
  wb, 
  sheet_name = "Panels", 
  output = table_panel
)

save_output_to_workbook(
  wb,
  sheet_name = "Probability",
  output = table_probability
)

save_output_to_workbook(
  wb, 
  sheet_name = "Follow up",
  output = table_followup
)
```

## export ——————————————————————————-

```{r}
data.frame(
  Sheet = seq_along(names(wb)),
  Worksheet = names(wb)
)
```

```{r}
#| warning: false

cat("Formatting worksheets...\n")

for (sheet in names(wb)) {
  
  cat("Formatting:", sheet, "\n")
  
  setColWidths(
    wb,
    sheet = sheet,
    cols = 1:30,
    widths = "auto"
  )
}

cat("Finished formatting worksheets.\n")
cat("Saving workbook...\n")

saveWorkbook(
  wb,
  excel_export_file_location,
  overwrite = TRUE
)

cat("Workbook saved successfully.\n")
```

## end ————————————————————————————

```{r}
print("end of script")
```
