---
title: "03-01-06-InfoSharingBinominal"
format: 
  html: {}
  pdf: {}
---

```{r}
source("../_common.R")
filtered_data <- readRDS("../artifacts/filtered_data.rds")
codebook <- readRDS("../artifacts/codebook.rds")
```

## setup

### libraries

```{r}
library(glmmTMB)
library(emmeans)
library(openxlsx)
library(modelsummary)
library(gtsummary)
library(broom)
```

```{r}
# Create workbook to save the analyses
wb <- createWorkbook()
excel_export_file_location <- "../artifacts/binomial_output.xlsx"

# Start fresh each time
if (file.exists(excel_export_file_location)) {
  file.remove(excel_export_file_location)
}
```

### items key

Each of the items from the tasks are listed by the variable name. A key is created with the characteristics of each item.

```{r}
item_vars <- c(
  "Q53_1", "Q53_2", "Q53_3", "Q53_4", "Q53_5", "Q53_6",
  "Q54_1", "Q54_2", "Q54_3", "Q54_4", "Q54_5", "Q54_6"
)

item_key <- tribble(
  ~ItemID,  ~InfoImportance, ~InfoDistribution,
  "Q53_1", "High",          "Common",
  "Q53_4", "High",          "Common",
  "Q53_5", "High",          "Common",
  "Q53_2", "Low",           "Common",
  "Q53_3", "Low",           "Common",
  "Q53_6", "Low",           "Common",
  "Q54_2", "High",          "Unique",
  "Q54_3", "High",          "Unique",
  "Q54_6", "High",          "Unique",
  "Q54_1", "Low",           "Unique",
  "Q54_4", "Low",           "Unique",
  "Q54_5", "Low",           "Unique"
)
```

### limit the data

Selects only the variables from the data set which will be used in the analysis.

```{r}
dat_items <- filtered_data %>%
  select(
    ResponseId,
    
    # experimental predictors
    structure_number01,
    motivation_number01,
    
    # control variables
    Q14.1,
    sex,
    SES_mean,
    hispanic,
    NeedCog_Mean,
    DirtyDozen_Narcissism,
    DirtyDozen_Psychopathy,
    DirtyDozen_Machiavellianism,
    SVO_angle,
    
    # individual information items
    Q53_1,
    Q53_2,
    Q53_3,
    Q53_4,
    Q53_5,
    Q53_6,
    Q54_1,
    Q54_2,
    Q54_3,
    Q54_4,
    Q54_5,
    Q54_6
  ) %>%
  mutate(
    across(
      c(
        Q53_1, Q53_2, Q53_3,
        Q53_4, Q53_5, Q53_6,
        Q54_1, Q54_2, Q54_3,
        Q54_4, Q54_5, Q54_6
      ),
      ~ case_when(
        .x %in% c(1, 3) ~ 0,
        .x == 2 ~ 1,
        TRUE ~ NA_real_
      )
    )
  )
```

### pivot

```{r}
dat_long <- dat_items %>%
  pivot_longer(
    cols = c(
      Q53_1, Q53_2, Q53_3,
      Q53_4, Q53_5, Q53_6,
      Q54_1, Q54_2, Q54_3,
      Q54_4, Q54_5, Q54_6
    ),
    names_to = "ItemID",
    values_to = "ItemResponse"
  )
```

### update labels

Adds meaningful labels to the key variables for easier interpretation later.

```{r}
# Combine key for items with data
# Update labels for variables
dat_long <- dat_long %>%
  left_join(item_key, by = "ItemID") %>%
  mutate(
    structure_number01 = factor(
      structure_number01,
      levels = c(0, 1),
      labels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      motivation_number01,
      levels = c(0, 1),
      labels = c("Proself", "Prosocial")
    ),
    InfoDistribution = factor(
      InfoDistribution,
      levels = c("Common", "Unique")
    ),
    InfoImportance = factor(
      InfoImportance,
      levels = c("High", "Low"),
      labels = c("High Importance", "Low Importance")
    )
  )
```

### checks

Are all of the items from the task prepsent?

```{r}
dat_long %>%
  distinct(
    ItemID,
    InfoImportance,
    InfoDistribution
  ) %>%
  arrange(ItemID)
```

Are there missing values?

```{r}
dat_long %>%
  filter(
    is.na(InfoImportance) |
    is.na(InfoDistribution)
  ) %>%
  distinct(ItemID)
```

Counting

```{r}
table(
  dat_long$InfoDistribution,
  dat_long$InfoImportance,
  useNA = "ifany"
)
```

```{r}
table(dat_long$ItemResponse, useNA = "ifany")
```

### save data

```{r}
# Export to excel file for sharing
write.xlsx(dat_long, "../artifacts/binominal_data.xlsx", asTable = TRUE, colWidths = "auto")
```

## control model

### create form

```{r}
#  This first part is only writing out the variables so that when I run the model it is easier to see the options in the model
form_controls <- ItemResponse ~ # ItemResponse is if the participant chose share or not share
  InfoDistribution +
  InfoImportance +
  Q14.1 + # 14.1 is age
  sex + # These are control variables
  SES_mean +
  hispanic +
  NeedCog_Mean +
  DirtyDozen_Narcissism +
  DirtyDozen_Psychopathy +
  DirtyDozen_Machiavellianism +
  SVO_angle +
  (1 | ResponseId) +
  (1 | ItemID)
```

```{r}
model_controls <- glmmTMB(
  form_controls,
  family = binomial(link = "logit"),
  data = dat_long
)

summary(model_controls)
```

```{r}
confint(model_controls)
```

Only sex and need for cognition were significant. Therefore, only these two control variables are kept in the full model.

#### table

```{r}
coef_table <- summary(model_controls)$coefficients$cond
ci <- confint(model_controls, parm = "beta_")

results <- data.frame(
  Predictor = rownames(coef_table),
  b = coef_table[, "Estimate"],
  SE = coef_table[, "Std. Error"],
  Wald_chisq = coef_table[, "z value"]^2,
  p = coef_table[, "Pr(>|z|)"],
  OR = exp(coef_table[, "Estimate"]),
  CI_lower = exp(ci[, 1]),
  CI_upper = exp(ci[, 2]),
  row.names = NULL
)

# Labels for dissertation table
predictor_labels <- c(
  "(Intercept)" = "Intercept",
  "InfoDistributionUnique" = "Common (0) vs. Unique (1)",
  "InfoImportanceLow Importance" = "Low (0) vs. High (1)",
  "Q14.1" = "Age",
  "sex" = "Sex (female = 1)",
  "SES_mean" = "Socioeconomic Status",
  "hispanic" = "Hispanic",
  "NeedCog_Mean" = "Need for Cognition",
  "DirtyDozen_Narcissism" = "Narcissism",
  "DirtyDozen_Psychopathy" = "Psychopathy",
  "DirtyDozen_Machiavellianism" = "Machiavellianism",
  "SVO_angle" = "SVO angle"
)

results$Predictor <- predictor_labels[results$Predictor]

# Add section rows
add_section <- function(label, template) {
  row <- template[1, ]
  row[] <- NA
  row$Predictor <- label
  row
}

results <- rbind(
  results,
  add_section("Within Participant Variables", results),
  add_section("Control Variables", results)
)

# Desired row order
row_order <- c(
  "Intercept",
  "Within Participant Variables",
  "Common (0) vs. Unique (1)",
  "Low (0) vs. High (1)",
  "Control Variables",
  "Age",
  "Sex (female = 1)",
  "Socioeconomic Status",
  "Hispanic",
  "Need for Cognition",
  "Narcissism",
  "Psychopathy",
  "Machiavellianism",
  "SVO angle"
)

final_results <- results[
  match(row_order, results$Predictor),
]

rownames(final_results) <- NULL

# Format regular statistics
stat_cols <- c("b", "SE", "Wald_chisq", "OR", "CI_lower", "CI_upper")

final_results[stat_cols] <-
  lapply(final_results[stat_cols], format_stat)

# Format p-values separately
final_results$p <-
  format_stat(final_results$p, p_value = TRUE)

# Combine OR and CI into one column
final_results$`OR [95% CI]` <- with(
  final_results,
  ifelse(
    OR == "",
    "",
    paste0(OR, " [", CI_lower, ", ", CI_upper, "]")
  )
)

# Remove separate OR and CI columns
final_results <- final_results[
  , !names(final_results) %in%
    c("OR", "CI_lower", "CI_upper")
]

controls_binomial <- final_results

rm(
  coef_table,
  ci,
  results,
  predictor_labels,
  row_order,
  stat_cols, 
  final_results
)

controls_binomial
```

###### 💾controls_binomial_table

```{r}
save_output_to_workbook(wb, "Control Variables", controls_binomial)
```

## full model

### create form

```{r}
#  This first part is only writing out the variables so that when I run the model it is easier to see the options in the model
form_binom <- ItemResponse ~ # ItemResponse is if the participant chose share or not share
  structure_number01 *
  motivation_number01 *
  InfoDistribution *
  InfoImportance +
  sex + # Only sex and NFC contributed to the model and were retained
  NeedCog_Mean +
  (1 | ResponseId) + # These are random intercepts to account for the participant's repeated responses to multiple clues and repeated answering across participants to the clues themselves
  (1 | ItemID)
```

### model

```{r}
# This second part is running the model
model_binom <- glmmTMB( # The package being used is glmmTMB
  form_binom, # This is the form that was created in the first step above
  family = binomial(link = "logit"), # Selects binomial distribution using logit link
  data = dat_long
)
```

```{r}
saveRDS(model_binom, 
        file = file.path("../artifacts/model_binom.rds")
        )
```

### table

```{r}
coef_table <- summary(model_binom)$coefficients$cond
ci <- confint(model_binom, parm = "beta_")

results <- data.frame(
  Predictor = rownames(coef_table),
  b = coef_table[, "Estimate"],
  SE = coef_table[, "Std. Error"],
  Wald_chisq = coef_table[, "z value"]^2,
  p = coef_table[, "Pr(>|z|)"],
  OR = exp(coef_table[, "Estimate"]),
  CI_lower = exp(ci[, 1]),
  CI_upper = exp(ci[, 2]),
  row.names = NULL
)

predictor_labels <- c(
  "(Intercept)" = "Intercept",

  "sex" =
    "Sex (1 = female)",

  "NeedCog_Mean" =
    "Need for Cognition",

  "structure_number01Intergroup" =
    "Interindividual (0) vs. Intergroup (1)",

  "motivation_number01Prosocial" =
    "Proself (0) vs. Prosocial (1)",

  "InfoDistributionUnique" =
    "Common (0) vs. Unique (1)",

  "InfoImportanceLow Importance" =
    "Low (0) vs. High (1)",

  "structure_number01Intergroup:motivation_number01Prosocial" =
    "Structure × Motivation",

  "structure_number01Intergroup:InfoDistributionUnique" =
    "Structure × Distribution",

  "motivation_number01Prosocial:InfoDistributionUnique" =
    "Motivation × Distribution",

  "structure_number01Intergroup:InfoImportanceLow Importance" =
    "Structure × Importance",

  "motivation_number01Prosocial:InfoImportanceLow Importance" =
    "Motivation × Importance",

  "InfoDistributionUnique:InfoImportanceLow Importance" =
    "Distribution × Importance",

  "structure_number01Intergroup:motivation_number01Prosocial:InfoDistributionUnique" =
    "Structure × Motivation × Distribution",

  "structure_number01Intergroup:motivation_number01Prosocial:InfoImportanceLow Importance" =
    "Structure × Motivation × Importance",

  "structure_number01Intergroup:InfoDistributionUnique:InfoImportanceLow Importance" =
    "Structure × Distribution × Importance",

  "motivation_number01Prosocial:InfoDistributionUnique:InfoImportanceLow Importance" =
    "Motivation × Distribution × Importance",

  "structure_number01Intergroup:motivation_number01Prosocial:InfoDistributionUnique:InfoImportanceLow Importance" =
    "Structure × Motivation × Distribution × Importance"
)

results$Predictor <- predictor_labels[results$Predictor]

add_section <- function(label, template) {
  row <- template[1, ]
  row[] <- NA
  row$Predictor <- label
  row
}

results <- rbind(
  results,
  add_section("Control Variables", results),
  add_section("Between Manipulations", results),
  add_section("Within Manipulations", results),
  add_section("Interactions", results)
)

row_order <- c(
  "Intercept",

  "Control Variables",
  "Sex (1 = female)",
  "Need for Cognition",

  "Between Manipulations",
  "Interindividual (0) vs. Intergroup (1)",
  "Proself (0) vs. Prosocial (1)",

  "Within Manipulations",
  "Common (0) vs. Unique (1)",
  "Low (0) vs. High (1)",

  "Interactions",
  "Structure × Motivation",
  "Structure × Distribution",
  "Motivation × Distribution",
  "Structure × Importance",
  "Motivation × Importance",
  "Distribution × Importance",
  "Structure × Motivation × Distribution",
  "Structure × Motivation × Importance",
  "Structure × Distribution × Importance",
  "Motivation × Distribution × Importance",
  "Structure × Motivation × Distribution × Importance"
)

final_model_results <- results[
  match(row_order, results$Predictor),
]

rownames(final_model_results) <- NULL

stat_cols <- c(
  "b",
  "SE",
  "Wald_chisq",
  "OR",
  "CI_lower",
  "CI_upper"
)

final_model_results[stat_cols] <-
  lapply(final_model_results[stat_cols], format_stat)

final_model_results$p <-
  format_stat(final_model_results$p, p_value = TRUE)

final_model_results$`OR [95% CI]` <- with(
  final_model_results,
  ifelse(
    OR == "",
    "",
    paste0(OR, " [", CI_lower, ", ", CI_upper, "]")
  )
)

final_model_results <- final_model_results[
  , !names(final_model_results) %in%
    c("OR", "CI_lower", "CI_upper")
]

model_binomial_table <- final_model_results
model_binomial_table
```

###### 💾model_binomial_table

```{r}
save_output_to_workbook(wb, "Binomial Table", model_binomial_table)
```

##### omnibus test

overall main effects and interactions

similar to Type III ANOVA-style table

```{r}
joint_results <- joint_tests(model_binom)

joint_results
```

## emmeans()

<https://rvlenth.github.io/emmeans/>

The purpose of this analysis is to break down the four-way interaction to understand what is happening with each of the variables.

Because `emmeans` with logistic models often reports contrasts as **odds ratios**, this will usually pair with the predicted probabilities from the bar chart.

These are means that are from the model, which means that they have all of the other predictor variables that were included in the model as well.

Also, random note about the package: the model was built with glmmTMB, so emmeans is relying on methods supplied by glmmTMB to tell it how to use the model data, fixed effects, covariance matrix, etc to compute the estimated marginal means.

<https://rdrr.io/r/stats/coef.html>

`coef()` is a generic function which extracts model coefficients from objects returned by modeling functions. coefficients is an alias for it.

`pairs()` is used on emmeans objects to probe significant effects or interactions

#### s \* m

```{r}
emm_sm <- emmeans(
  model_binom,
  ~ structure_number01 * motivation_number01 |
    InfoDistribution * InfoImportance,
  type = "response"
)
```

###### 💾emm_sm

```{r}
save_output_to_workbook(wb, "SM emmean", emm_sm)
```

##### pairs()

```{r}
pairs(
  emm_sm, 
  adjust = "holm"
  )
```

###### 💾 contrasts_emm_sm

```{r}
save_output_to_workbook(
  wb, 
  sheet_name = "SM Pairs", 
  output = 
    pairs(
      emm_sm, 
      adjust = "holm"
      )
    )

```

##### 📊fig_emm_sm

```{r}
emm_sm_df <- as.data.frame(emm_sm)
```

```{r}
fig_emm_sm <- ggplot(
  emm_sm_df,
  aes(
    x = structure_number01,
    y = prob,
    fill = motivation_number01
  )
) +
  geom_col(
    position = position_dodge(width = 0.9)
  ) +
  geom_errorbar(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL
    ),
    width = 0.2,
    position = position_dodge(width = 0.9)
  ) +
  facet_grid(
    InfoDistribution ~ InfoImportance
  ) +
  labs(
    x = "Structure",
    y = "Predicted Probability of Sharing",
    fill = "Motivation"
  )

fig_emm_sm
```

###### 💾 fig_emm_sm

```{r}
# Where to save and worksheet name
sheet_name  <- "SM Figure"
figure_file <- "../artifacts/SM_Interaction.png" 
figure_name <- fig_emm_sm
```

```{r}
save_figure_to_workbook(
    wb,
    sheet_name ,
    figure_name,
    figure_file,
    width = 8,
    height = 6,
    dpi = 300
)
```

#### m

Within a specific combination of structure, distribution, and importance, does Proself differ from Prosocial?

```{r}
emm_mot <- emmeans(
  model_binom,
  ~ motivation_number01 |
    structure_number01 *
    InfoDistribution *
    InfoImportance,
  type = "response"
)

pairs(
  emm_mot, 
  adjust = "holm")
```

#### s

Within a specific motivation, distribution, and importance condition, does Interindividual differ from Intergroup?

```{r}
emm_struct <- emmeans(
  model_binom,
  ~ structure_number01 |
    motivation_number01 *
    InfoDistribution *
    InfoImportance,
  type = "response"
)

pairs(
  emm_struct,
  adjust = "holm"
  )
```

#### high imp & unique

```{r}
emm_high_unique <- emmeans(
  model_binom,
  ~ structure_number01 * motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

emm_high_unique
```

Are those two structure differences themselves significantly different from one another? No, there is insufficient evidence that the structure effect is statistically different between Proself and Prosocial. Shown in the contrast below.

```{r}
pairs(
  emm_high_unique, 
  adjust = "holm"
)
```

#### high imp & unique & structure

Among prosocial participants, is the intergroup different from the interindividual? (And also, among the proself participants, is the intergroup different from the interindividual?)

Yes, there is a significant different among Prosocial participants. (simple effect of structure?)

Among prosocial participants, the predicted probability of sharing high-importance, unique information was significantly higher in the interindividual condition (.722) than in the intergroup condition (.445), OR = 3.24, p = .003.

```{r}
emm_high_unique_structure <- emmeans(
  model_binom,
  ~ structure_number01 |
    motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

pairs(
  emm_high_unique_structure,
  adjust = "holm"
)
```

###### 💾HU Prosocial emmean

```{r}
save_output_to_workbook(
  wb, 
  "HU Prosocial emmean", 
  emm_high_unique_structure
)
```

###### 💾HU Prosocial Contrast

```{r}
save_output_to_workbook(
  wb, 
  sheet_name = "HU Prosocial Contrast", 
  output =  pairs(
              emm_high_unique_structure,
              adjust = "holm"
            )
)
```

### joint_tests()

#### info importance & info distribution

```{r}
joint_panels <- joint_tests(
  model_binom,
  by = c("InfoImportance", "InfoDistribution")
)

joint_panels
```

| Information condition | Structure | Motivation | Structure × Motivation | What it means |
|---------------|---------------|---------------|---------------|---------------|
| **High, Common** | .869 | **\< .001** | **\< .001** | The effect of structure depends on motivation. Unpack with simple interactions. |
| **High, Unique** | **.004** | **\< .001** | .246 | Structure and motivation both have significant effects, with [no]{.underline} evidence that their effects depend on one another. |
| **Low, Common** | .273 | .185 | .110 | [No]{.underline} significant effects of structure, motivation, or their interaction. |
| **Low, Unique** | .618 | .051 | .210 | [No]{.underline} significant effects at the conventional .05 level. Motivation is close, but does not reach significance. |

```{r}
save_output_to_workbook(
  wb, 
  sheet_name = "Joint Panels", 
  output = joint_panels
)
```

##### emmeans()

Explore the significant panels

-   High/Common

-   High/Unique

###### High/Common

```{r}
emm_high_common <- emmeans(
  model_binom,
  ~ structure_number01 * motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Common"
  ),
  type = "response"
)
```

compare Structure within each Motivation

```{r}
pairs(
  emmeans(
    model_binom,
    ~ structure_number01 | motivation_number01,
    at = list(
      InfoImportance = "High Importance",
      InfoDistribution = "Common"
    ),
    type = "response"
  ),
  adjust = "holm"
)
```

compare Motivation within each Structure

```{r}
pairs(
  emmeans(
    model_binom,
    ~ motivation_number01 | structure_number01,
    at = list(
      InfoImportance = "High Importance",
      InfoDistribution = "Common"
    ),
    type = "response"
  ),
  adjust = "holm"
)
```

###### High/Unique

overall difference between Interindividual and Intergroup

```{r}
emmeans(
  model_binom,
  pairwise ~ structure_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response",
  adjust = "holm"
)
```

overall difference between Proself and Prosocial

```{r}
emmeans(
  model_binom,
  pairwise ~ motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response",
  adjust = "holm"
)
```

## Save to excel

```{r}
saveWorkbook(
  wb,
  excel_export_file_location,
  overwrite = TRUE
)
```

## End

```{r}
print("end of script")
```
