---
title: "reasonsForChoices"
format: html
---

```{r}
filtered_data <- readRDS("../artifacts/filtered_data.rds")
codebook <- readRDS("../artifacts/codebook.rds")
source("../_common.R")
```

```{r}
# libraries
library(psych)
library(dplyr)
library(glmtoolbox)
library(dplyr)
library(forcats)
library(purrr)
library(broom)  
library(emmeans)
library(igraph)
library(qgraph)
library(Matrix)
```

## 4. REASONS FOR CHOICES

### vars

#### conditions

```{r}
vars_conditions <- c(
  "condition",
  "structure",
  "structure_number01",
  "motivation",
  "motivation_number01"
)
```

#### all

```{r}
vars_reasons_all <- c(
  "REASONS_1",
  "REASONS_2",
  "REASONS_3",
  "REASONS_4",
  "REASONS_5",
  "REASONS_6",
  "REASONS_7",
  "REASONS_8"
)
```

#### coOperation

```{r}
vars_reasons_coOp <- c(
  "REASONS_1",
  "REASONS_2",
  "REASONS_3"
)
```

#### coMpetition

```{r}
vars_reasons_coMp <- c(
  "REASONS_4",
  "REASONS_5",
  "REASONS_6",
  "REASONS_7",
  "REASONS_8"
)
```

### correlations

#### all - spearman

```{r}
cor_mat <- corr_table(filtered_data, vars_reasons_all, vars_reasons_all, "spearman")

cor_mat
```

#### coOperation

```{r}
corr_table(filtered_data, vars_reasons_coOp, vars_reasons_coOp, "spearman")
```

#### coMpetition

```{r}
corr_table(filtered_data, vars_reasons_coMp, vars_reasons_coMp, "spearman")
```

### create subset of data

must create dataset with only variables of interest to run alpha

#### all

```{r}
data_reasons_all <- filtered_data %>% 
  dplyr::select(all_of(vars_reasons_all))
```

#### coOperation

```{r}
data_reasons_coOp <- filtered_data %>% 
  dplyr::select(all_of(vars_reasons_coOp))
```

#### coMpetition

```{r}
data_reasons_coMp <- filtered_data %>% 
  dplyr::select(all_of(vars_reasons_coMp))
```

#### counts of endorsement per participant

```{r}
endorse_counts <- filtered_data %>%
  mutate(
    coop_total = rowSums(across(all_of(vars_reasons_coOp)), na.rm = TRUE),
    comp_total = rowSums(across(all_of(vars_reasons_coMp)), na.rm = TRUE)
  ) %>%
  select(any_of(vars_conditions), any_of(c("ResponseId")),
         all_of(vars_reasons_coOp), all_of(vars_reasons_coMp),
         coop_total, comp_total)
```

#### proportion of count

```{r}
endorse_counts <- endorse_counts %>%
  mutate(
    coop_prop = coop_total / length(vars_reasons_coOp),
    comp_prop = comp_total / length(vars_reasons_coMp)
  )
```

#### count z-score

```{r}
endorse_counts <- endorse_counts %>%
  mutate(
    coop_z = scale(coop_total),
    comp_z = scale(comp_total)
  )
```

### alpha

uses psych library

#### all

```{r}
psych::alpha(data_reasons_all)
```

#### coOperation

```{r}
psych::alpha(data_reasons_coOp)
```

#### coMpetition

```{r}
psych::alpha(data_reasons_coMp)
```

### descriptives

#### all

```{r}
summarise_numeric(filtered_data, vars_reasons_all)
```

#### frequencies

```{r}
# data_reasons_all


endorse_freq <- data_reasons_all %>%
  pivot_longer(
    everything(),
    names_to = "Item",
    values_to = "Endorsed"
  ) %>%
  group_by(Item) %>%
  summarise(
    n_endorsed = sum(Endorsed == 1, na.rm = TRUE),
    prop_endorsed = mean(Endorsed == 1, na.rm = TRUE)
  ) %>%
  ungroup()

endorse_freq
```

#### counts

```{r}
endorse_count_summary <- endorse_counts %>%
  summarise(
    M_coop = mean(coop_total, na.rm = TRUE),
    SD_coop = sd(coop_total, na.rm = TRUE),
    M_comp = mean(comp_total, na.rm = TRUE),
    SD_comp = sd(comp_total, na.rm = TRUE)
  )

endorse_count_summary
```

### cross-tab condition

#### means and sd

```{r}
desc_tbl <- map_dfr(vars_reasons_all, desc_by_cell)
desc_tbl
```

```{r}
var_order <- vars_reasons_all

cond_order <- c(                           # put the columns how you want them
  "individual–prosocial",
  "individual–proself",
  "group–prosocial",
  "group–proself"
)

# 2) prep, set factor levels for ordering, and pivot wide
apa_tbl <- desc_tbl %>%
  mutate(
    condition = paste(structure, motivation, sep = "–"),
    condition = factor(condition, levels = cond_order),
    variable  = factor(variable,  levels = var_order),
    cell      = sprintf("%.2f (%.2f)", M, SD)
  ) %>%
  dplyr::select(variable, condition, cell) %>%
  tidyr::pivot_wider(names_from = condition, values_from = cell) %>%
  arrange(variable) %>%                     # rows follow var_order
  dplyr::select(variable, any_of(cond_order))      # columns follow cond_order

apa_tbl
```

#### count

```{r}
endorse_counts_by_condition <- endorse_counts %>%
  group_by(condition) %>%
  summarise(
    Coop = paste0(
      round(mean(coop_total, na.rm = TRUE), 2), 
      " (", round(sd(coop_total, na.rm = TRUE), 2), ")"
    ),
    Comp = paste0(
      round(mean(comp_total, na.rm = TRUE), 2), 
      " (", round(sd(comp_total, na.rm = TRUE), 2), ")"
    ),
    n = dplyr::n(),
    .groups = "drop"
  )

endorse_counts_by_condition
```

#### proportion of count

```{r}
endorse_countsprop_by_condition <- endorse_counts %>%
  group_by(condition) %>%
  summarise(
    Coop = paste0(
      round(mean(coop_prop, na.rm = TRUE), 2), 
      " (", round(sd(coop_prop, na.rm = TRUE), 2), ")"
    ),
    Comp = paste0(
      round(mean(comp_prop, na.rm = TRUE), 2), 
      " (", round(sd(comp_prop, na.rm = TRUE), 2), ")"
    ),
    n = dplyr::n(),
    .groups = "drop"
  )

endorse_countsprop_by_condition
```

### 🗑️wide data

GEE requires long data, rather than wide data

```{r}
# Limit variables to those that should be inlcuded in the long dataframe
data_reasons_wide <- filtered_data %>%
  dplyr::select(
    "ResponseId",
    "structure",
    "motivation",
    "structure_number01",
    "motivation_number01",
    "Q14.1",
    "sex",
    "SES_mean",
    "NeedCog_Mean",
    "DirtyDozen_Narcissism",
    "DirtyDozen_Psychopathy",
    "DirtyDozen_Machiavellianism",
    "DirtyDozen_Mean",
    "SVO_angle",
    "Manipulation_Mean",
    "hispanic",
    "REASONS_1",
    "REASONS_2",
    "REASONS_3",
    "REASONS_4",
    "REASONS_5",
    "REASONS_6",
    "REASONS_7",
    "REASONS_8"
  )

```

```{r}
item_key <- tibble(
  ItemCode  = vars_reasons_all,
  Frame = c("coOp","coOp","coOp","coMp","coMp","coMp","coMp","coMp"),
  ItemLabel = c("Trusted others would share",
            "Commitment to share",
            "Solve the problem (intrinsic)",
            "Did not want to lose",
            "Exploit others’ sharing",
            "Did not trust others",
            "Avoid being exploited",
            "Don’t let others do better")
)
```

```{r}
# Convert to long dataframe
data_reasons_long <- data_reasons_wide %>%
  pivot_longer(
    cols = all_of(vars_reasons_all),
    names_to  = "ItemCode",
    values_to = "Endorse"
  ) %>%
  left_join(item_key, by = "ItemCode") %>%
  mutate(
    Frame     = factor(Frame, levels = c("coOp","coMp")),
    ItemCode  = factor(ItemCode, levels = vars_reasons_all),
    structure = factor(structure),
    motivation= factor(motivation),
    ResponseId= factor(ResponseId),
    Age       = suppressWarnings(as.numeric(Q14.1)),
    Sex       = factor(sex),
    SES_mean  = suppressWarnings(as.numeric(SES_mean)),
    NeedCog_Mean = suppressWarnings(as.numeric(NeedCog_Mean)),
    DirtyDozen_Narcissism       = suppressWarnings(as.numeric(DirtyDozen_Narcissism)),
    DirtyDozen_Psychopathy      = suppressWarnings(as.numeric(DirtyDozen_Psychopathy)),
    DirtyDozen_Machiavellianism = suppressWarnings(as.numeric(DirtyDozen_Machiavellianism)),
    SVO_angle = suppressWarnings(as.numeric(SVO_angle))
  ) %>%
  dplyr::select(ResponseId, structure, motivation, Frame, ItemCode, ItemLabel, Endorse, everything())


# View(data_reasons_long)
```

#### coOp data

```{r}
data_reasons_long_coop <- data_reasons_long %>%
  dplyr::filter(Frame == "coOp") %>%
  dplyr::mutate(
    Frame    = droplevels(Frame),
    ItemCode = droplevels(ItemCode)
  )

```

#### coMp data

```{r}
data_reasons_long_comp <- data_reasons_long %>%
  dplyr::filter(Frame == "coMp") %>%
  dplyr::mutate(
    Frame    = droplevels(Frame),
    ItemCode = droplevels(ItemCode)
  )

```

### 🟧logistic regression

create division between the two frames used in the items: cooperation and competition

#### control variables

```{r}
form_controls <- Endorse ~ 
  Q14.1 + Sex + SES_mean + hispanic +
  NeedCog_Mean + 
  DirtyDozen_Narcissism +
  DirtyDozen_Psychopathy +
  DirtyDozen_Machiavellianism +
  SVO_angle
```

##### all

```{r}
gee_reason_controls <- glmgee(
  form_controls,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason_controls, corr.digits=2, varest="bias-corrected")
```

```{r}
model_summary <- gee_reason_controls

# Calculate Cook's Distance for participants (clusters)
cd_cl_mat <- cooks.distance(
  model_summary,
  method  = "full",
  level   = "clusters",
  plot.it = FALSE
)

# Extract numeric values
cd_cl <- as.numeric(cd_cl_mat[, 1])

# Get the participant IDs in the exact order glmgee used
cluster_ids <- unique(model_summary$id)

# Build the table
cooks_table <- data.frame(
  ResponseId = cluster_ids,
  CooksD     = cd_cl
)

# Add a cutoff flag
cutoff <- 4 / length(cluster_ids)
cooks_table$Flag <- cooks_table$CooksD > cutoff

# Show the flagged participants
subset(cooks_table, Flag)
```

##### coOperation

```{r}
gee_reason__coOp_controls <- glmgee(
  form_controls,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long_coop,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason__coOp_controls, corr.digits=2, varest="bias-corrected")
```

```{r}
model_summary <- gee_reason__coOp_controls

# Calculate Cook's Distance for participants (clusters)
cd_cl_mat <- cooks.distance(
  model_summary,
  method  = "full",
  level   = "clusters",
  plot.it = FALSE
)

# Extract numeric values
cd_cl <- as.numeric(cd_cl_mat[, 1])

# Get the participant IDs in the exact order glmgee used
cluster_ids <- unique(model_summary$id)

# Build the table
cooks_table <- data.frame(
  ResponseId = cluster_ids,
  CooksD     = cd_cl
)

# Add a cutoff flag
cutoff <- 4 / length(cluster_ids)
cooks_table$Flag <- cooks_table$CooksD > cutoff

# Show the flagged participants
subset(cooks_table, Flag)
```

##### coMpetition

```{r}
gee_reason__coMp_controls <- glmgee(
  form_controls,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long_comp,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason__coMp_controls, corr.digits=2, varest="bias-corrected")
```

```{r}
model_summary <- gee_reason__coMp_controls

# Calculate Cook's Distance for participants (clusters)
cd_cl_mat <- cooks.distance(
  model_summary,
  method  = "full",
  level   = "clusters",
  plot.it = FALSE
)

# Extract numeric values
cd_cl <- as.numeric(cd_cl_mat[, 1])

# Get the participant IDs in the exact order glmgee used
cluster_ids <- unique(model_summary$id)

# Build the table
cooks_table <- data.frame(
  ResponseId = cluster_ids,
  CooksD     = cd_cl
)

# Add a cutoff flag
cutoff <- 4 / length(cluster_ids)
cooks_table$Flag <- cooks_table$CooksD > cutoff

# Show the flagged participants
subset(cooks_table, Flag)
```

#### 🟧models

models with the conditions included

```{r}
form_model <- Endorse ~ structure_number01 * motivation_number01 + Q14.1 
```

##### coOperation

```{r}
gee_reason_coOp <- glmgee(
  form_model,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long_coop,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason_coOp, corr.digits=2, varest="bias-corrected")
```

```{r}
model_summary <- gee_reason_coOp

# Calculate Cook's Distance for participants (clusters)
cd_cl_mat <- cooks.distance(
  model_summary,
  method  = "full",
  level   = "clusters",
  plot.it = FALSE
)

# Extract numeric values
cd_cl <- as.numeric(cd_cl_mat[, 1])

# Get the participant IDs in the exact order glmgee used
cluster_ids <- unique(model_summary$id)

# Build the table
cooks_table <- data.frame(
  ResponseId = cluster_ids,
  CooksD     = cd_cl
)

# Add a cutoff flag
cutoff <- 4 / length(cluster_ids)
cooks_table$Flag <- cooks_table$CooksD > cutoff

# Show the flagged participants
subset(cooks_table, Flag)
```

###### drop cases

```{r}
# Put IDs to drop below
drop_ids <- c(
  "R_2wpBqhR7RBKSVMh",
  "R_9NZOvLNPLr5aXYJ",
  "R_2f3rqwY85h48vEW",
  "R_2TsN65JNPpI1Z2p",
  "R_1IAHkeMQfTPGbXe"
)

data_reasons_long_coop <- data_reasons_long_coop %>%
  filter(!ResponseId %in% drop_ids)

print("dropped")
```

###### rerun

```{r}
gee_reason_coOp <- glmgee(
  form_model,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long_coop,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason_coOp, corr.digits=2, varest="bias-corrected")
```

###### Table: model coMp

```{r}
model <- gee_reason_coOp

# Get coefficient table from your fitted model
coef_table <- summary(model, corr.digits=2, varest="bias-corrected")$coefficients

# Pull out estimates, SEs, and p-values
est <- coef_table[, "Estimate"]
se  <- coef_table[, "Std.Error"]   # <- capital E
p   <- coef_table[, "Pr(>|z|)"]    # <- not W, but z

# Compute IRR (odds ratio)
irr <- exp(est)

# Compute 95% CI for IRR
lower <- exp(est - 1.96 * se)
upper <- exp(est + 1.96 * se)

# Put into one table
results <- data.frame(
  Estimate = round(est, 2),
  SE       = round(se, 2),
  p_value  = signif(p, 2),
  IRR      = round(irr, 2),
  CI       = paste0("[", round(lower, 2), ", ", round(upper, 2), "]")
)

print(results)
```

##### coMpetition

```{r}
gee_reason_coMp <- glmgee(
  form_model,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long_comp,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason_coMp, corr.digits=2, varest="bias-corrected")
```

```{r}
model_summary <- gee_reason_coMp

# Calculate Cook's Distance for participants (clusters)
cd_cl_mat <- cooks.distance(
  model_summary,
  method  = "full",
  level   = "clusters",
  plot.it = FALSE
)

# Extract numeric values
cd_cl <- as.numeric(cd_cl_mat[, 1])

# Get the participant IDs in the exact order glmgee used
cluster_ids <- unique(model_summary$id)

# Build the table
cooks_table <- data.frame(
  ResponseId = cluster_ids,
  CooksD     = cd_cl
)

# Add a cutoff flag
cutoff <- 4 / length(cluster_ids)
cooks_table$Flag <- cooks_table$CooksD > cutoff

# Show the flagged participants
subset(cooks_table, Flag)
```

###### drop cases

```{r}
# Put IDs to drop below
drop_ids <- c(
"R_2wpBqhR7RBKSVMh",
"R_87Ew3rN6MShE6CB",
"R_1LiHDxMhn1OjVXz",
"R_DTOIxAq5bZIHbGx",
"R_CazljxynrmgmA4F",
"R_3kiDUZJ8TlKyVob",
"R_2xWAwczrTQNRrgi"
)

data_reasons_long_comp <- data_reasons_long_comp %>%
  filter(!ResponseId %in% drop_ids)

print("dropped")
```

###### rerun

```{r}
gee_reason_coMp <- glmgee(
  form_model,
  id     = ResponseId,          
  family = binomial("logit"),
  data   = data_reasons_long_comp,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_reason_coMp, corr.digits=2, varest="bias-corrected")
```

```{r}
model <- gee_reason_coMp

# Get coefficient table from your fitted model
coef_table <- summary(model, corr.digits=2, varest="bias-corrected")$coefficients

# Pull out estimates, SEs, and p-values
est <- coef_table[, "Estimate"]
se  <- coef_table[, "Std.Error"]   # <- capital E
p   <- coef_table[, "Pr(>|z|)"]    # <- not W, but z

# Compute IRR (odds ratio)
irr <- exp(est)

# Compute 95% CI for IRR
lower <- exp(est - 1.96 * se)
upper <- exp(est + 1.96 * se)

# Put into one table
results <- data.frame(
  Estimate = round(est, 2),
  SE       = round(se, 2),
  p_value  = signif(p, 2),
  IRR      = round(irr, 2),
  CI       = paste0("[", round(lower, 2), ", ", round(upper, 2), "]")
)

print(results)
```

```{r}
g <- graph_from_adjacency_matrix(co_prop, weighted = TRUE, diag = FALSE)
plot(g, edge.width = E(g)$weight * 10)  
# thicker edges = stronger co-occurrence

```

------------------------------------------------------------------------

## END

```{r}
print("All done!")
```
