---
title: "informationSharing"
format: html
---

```{r}
filtered_data <- readRDS("../artifacts/filtered_data.rds")
gee_long_all_bx <- readRDS("../artifacts/gee_long_all_bx.rds")
gee_long_non <- readRDS("../artifacts/gee_long_non.rds")
gee_long_shared <- readRDS("../artifacts/gee_long_shared.rds")
combined_data <- readRDS("../artifacts/combined_data.rds")
source("../_common.R")
```

```{r}
#| message: false
#| warning: false
# Libraries
library(glmtoolbox)
library(geepack)
library(glmmTMB)
```

## ---- INFORMATION SHARING TASK ----

Note: cases were dropped that were flags in the drop-cases file.

This version uses GEE Poisson and COM-Poisson. In both analyzes, the signiicant control variables are the same: sex and need for cognition.

## control variables

### form_controls

```{r}
# 1) Write your formula (drop Behavior if you're on shared-only data)
form_controls <- Count ~ InfoType + InfoImportance +
  Q14.1 + Sex + SES_mean + hispanic +
  NeedCog_Mean + 
  DirtyDozen_Narcissism +
  DirtyDozen_Psychopathy +
  DirtyDozen_Machiavellianism +
  SVO_angle
```

```{r}
form_mixed <- update(form_controls, . ~ . + (1 | ResponseId))
```

### label variables

### create dat

```{r}
# 2) Build a complete-cases analysis data set for exactly these vars + id
vars_needed <- c("ResponseId", all.vars(form_controls))

dat <- gee_long_shared %>%
  # make sure there are no character columns sneaking in
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

```{r}
# Sanity checks
stopifnot(nrow(dat) > 0)
stopifnot(!any(is.na(dat$ResponseId)))
# Make sure each factor in RHS has ≥2 levels
sapply(dat[setdiff(all.vars(form_controls), c("Count"))], function(x)
  if (is.factor(x)) nlevels(x) else NA_integer_) -> fac_lvls
fac_lvls[!is.na(fac_lvls)]
```

## test controls

### GEE

```{r}
# 3) Fit the GEE on the filtered data
gee_model_controls <- glmgee(
  form_controls,
  id     = ResponseId,          
  family = poisson(link = "log"),
  data   = dat,
  corstr = "exchangeable",
  na.action = na.omit,
)

summary(gee_model_controls)
```

#### cook's distance

```{r}
# Calculate Cook's Distance for participants (clusters)
cd_cl_mat <- cooks.distance(
  gee_model_controls,
  method  = "full",
  level   = "clusters",
  plot.it = FALSE
)

# Extract numeric values
cd_cl <- as.numeric(cd_cl_mat[, 1])

# Get the participant IDs in the exact order glmgee used
cluster_ids <- unique(gee_model_controls$id)

# Build the table
cooks_table <- data.frame(
  ResponseId = cluster_ids,
  CooksD     = cd_cl
)

# Add a cutoff flag
cutoff <- 4 / length(cluster_ids)
cooks_table$Flag <- cooks_table$CooksD > cutoff

# Show the flagged participants
subset(cooks_table, Flag)
```

### rerun model

hide z, and ci for estimate.

controls to include:

age, sex, need for cognition, narcissism (trend)

```{r}
levels(gee_long_shared$InfoType)
# levels(gee_long_shared$InfoImportance)
```

## COM-Poisson

```{r}
model_mixedCOM <- glmmTMB(form_mixed,
               family = compois(),
               data = dat
)

summary(model_mixedCOM)
```

## ---End of Page---

```{r}
print("All done!")
```
