---
title: "03-01-06-InfoSharingBinominal"
format: 
  html: {}
  pdf: {}
---

```{r}
#| warning: false
source("../_common.R")
filtered_data <- readRDS("../artifacts/filtered_data.rds")
codebook <- readRDS("../artifacts/codebook.rds")
```

## setup —————————————-

### libraries

```{r}
#| warning: false
library(glmmTMB)
library(emmeans)
library(openxlsx)
library(modelsummary)
library(gtsummary)
library(broom)
library(DHARMa)
library(papaja)
library(RColorBrewer)
library(tibble)
```

```{r}
# Create workbook to save the analyses
wb <- createWorkbook()
excel_export_file_location <- "../artifacts/binomial_output.xlsx"

# Start fresh each time
if (file.exists(excel_export_file_location)) {
  file.remove(excel_export_file_location)
}
```

### items key

Each of the items from the tasks are listed by the variable name. A key is created with the characteristics of each item.

```{r}
item_vars <- c(
  "Q53_1", "Q53_2", "Q53_3", "Q53_4", "Q53_5", "Q53_6",
  "Q54_1", "Q54_2", "Q54_3", "Q54_4", "Q54_5", "Q54_6"
)

item_key <- tribble(
  ~ItemID,  ~InfoImportance, ~InfoDistribution,
  "Q53_1", "High",          "Common",
  "Q53_4", "High",          "Common",
  "Q53_5", "High",          "Common",
  "Q53_2", "Low",           "Common",
  "Q53_3", "Low",           "Common",
  "Q53_6", "Low",           "Common",
  "Q54_2", "High",          "Unique",
  "Q54_3", "High",          "Unique",
  "Q54_6", "High",          "Unique",
  "Q54_1", "Low",           "Unique",
  "Q54_4", "Low",           "Unique",
  "Q54_5", "Low",           "Unique"
)
```

### limit the data

Selects only the variables from the data set which will be used in the analysis.

```{r}
dat_items <- filtered_data %>%
  select(
    ResponseId,
    
    # experimental predictors
    structure_number01,
    motivation_number01,
    
    # control variables
    Q14.1,
    sex,
    SES_mean,
    hispanic,
    NeedCog_Mean,
    DirtyDozen_Narcissism,
    DirtyDozen_Psychopathy,
    DirtyDozen_Machiavellianism,
    SVO_angle,
    
    # individual information items
    Q53_1,
    Q53_2,
    Q53_3,
    Q53_4,
    Q53_5,
    Q53_6,
    Q54_1,
    Q54_2,
    Q54_3,
    Q54_4,
    Q54_5,
    Q54_6
  ) %>%
  mutate(
    across(
      c(
        Q53_1, Q53_2, Q53_3,
        Q53_4, Q53_5, Q53_6,
        Q54_1, Q54_2, Q54_3,
        Q54_4, Q54_5, Q54_6
      ),
      ~ case_when(
        .x %in% c(1, 3) ~ 0,
        .x == 2 ~ 1,
        TRUE ~ NA_real_
      )
    )
  )
```

### pivot

Data restructuring from wide to long.

```{r}
dat_long <- dat_items %>%
  pivot_longer(
    cols = c(
      Q53_1, Q53_2, Q53_3,
      Q53_4, Q53_5, Q53_6,
      Q54_1, Q54_2, Q54_3,
      Q54_4, Q54_5, Q54_6
    ),
    names_to = "ItemID",
    values_to = "ItemResponse"
  )
```

### update labels

Adds meaningful labels to the key variables for easier interpretation later.

```{r}
# Combine key for items with data
# Update labels for variables
dat_long <- dat_long %>%
  left_join(item_key, by = "ItemID") %>%
  mutate(
    structure_number01 = factor(
      structure_number01,
      levels = c(0, 1),
      labels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      motivation_number01,
      levels = c(0, 1),
      labels = c("Proself", "Prosocial")
    ),
    InfoDistribution = factor(
      InfoDistribution,
      levels = c("Common", "Unique")
    ),
    InfoImportance = factor(
      InfoImportance,
      levels = c("Low", "High"),
      labels = c("Low Importance", "High Importance")
    )
  )
```

### checks

Are all of the items from the task present?

```{r}
dat_long %>%
  distinct(
    ItemID,
    InfoImportance,
    InfoDistribution
  ) %>%
  arrange(ItemID)
```

Are there missing values?

```{r}
dat_long %>%
  filter(
    is.na(InfoImportance) |
    is.na(InfoDistribution)
  ) %>%
  distinct(ItemID)
```

Counting

```{r}
table(
  dat_long$InfoDistribution,
  dat_long$InfoImportance,
  useNA = "ifany"
)
```

```{r}
table(dat_long$ItemResponse, useNA = "ifany")
```

### save data

```{r}
# Export to excel file for sharing
write.xlsx(dat_long, "../artifacts/binominal_data.xlsx", asTable = TRUE, colWidths = "auto")
```

## control model —————————————-

### create form

```{r}
#  This first part is only writing out the variables so that when I run the model it is easier to see the options in the model
form_controls <- ItemResponse ~ # ItemResponse is if the participant chose share or not share
  InfoDistribution +
  InfoImportance +
  Q14.1 + # 14.1 is age
  sex + # These are control variables
  SES_mean +
  hispanic +
  NeedCog_Mean +
  DirtyDozen_Narcissism +
  DirtyDozen_Psychopathy +
  DirtyDozen_Machiavellianism +
  SVO_angle +
  (1 | ResponseId) +
  (1 | ItemID)
```

```{r}
model_controls <- glmmTMB(
  form_controls,
  family = binomial(link = "logit"),
  data = dat_long
)

summary(model_controls)
```

```{r}
confint(model_controls)
```

#### table

```{r}
coef_table <- summary(model_controls)$coefficients$cond
ci <- confint(model_controls, parm = "beta_")

results <- data.frame(
  Predictor = rownames(coef_table),
  b = coef_table[, "Estimate"],
  SE = coef_table[, "Std. Error"],
  Wald_chisq = coef_table[, "z value"]^2,
  p = coef_table[, "Pr(>|z|)"],
  OR = exp(coef_table[, "Estimate"]),
  CI_lower = exp(ci[, 1]),
  CI_upper = exp(ci[, 2]),
  row.names = NULL
)

# Labels for dissertation table
predictor_labels <- c(
  "(Intercept)" = "Intercept",
  "InfoDistributionUnique" = "Common (0) vs. Unique (1)",
  "InfoImportanceHigh Importance" = "Low (0) vs. High (1)",
  "Q14.1" = "Age",
  "sex" = "Sex (female = 1)",
  "SES_mean" = "Socioeconomic Status",
  "hispanic" = "Hispanic",
  "NeedCog_Mean" = "Need for Cognition",
  "DirtyDozen_Narcissism" = "Narcissism",
  "DirtyDozen_Psychopathy" = "Psychopathy",
  "DirtyDozen_Machiavellianism" = "Machiavellianism",
  "SVO_angle" = "SVO angle"
)

results$Predictor <- predictor_labels[results$Predictor]

# Add section rows
add_section <- function(label, template) {
  row <- template[1, ]
  row[] <- NA
  row$Predictor <- label
  row
}

results <- rbind(
  results,
  add_section("Within Participant Variables", results),
  add_section("Control Variables", results)
)

# Desired row order
row_order <- c(
  "Intercept",
  "Within Participant Variables",
  "Common (0) vs. Unique (1)",
  "Low (0) vs. High (1)",
  "Control Variables",
  "Age",
  "Sex (female = 1)",
  "Socioeconomic Status",
  "Hispanic",
  "Need for Cognition",
  "Narcissism",
  "Psychopathy",
  "Machiavellianism",
  "SVO angle"
)

final_results <- results[
  match(row_order, results$Predictor),
]

rownames(final_results) <- NULL

# Format regular statistics
stat_cols <- c("b", "SE", "Wald_chisq", "OR", "CI_lower", "CI_upper")

final_results[stat_cols] <-
  lapply(final_results[stat_cols], format_stat)

# Format p-values separately
final_results$p <-
  format_stat(final_results$p, p_value = TRUE)

# Combine OR and CI into one column
final_results$`OR [95% CI]` <- with(
  final_results,
  ifelse(
    OR == "",
    "",
    paste0(OR, " [", CI_lower, ", ", CI_upper, "]")
  )
)

# Remove separate OR and CI columns
final_results <- final_results[
  , !names(final_results) %in%
    c("OR", "CI_lower", "CI_upper")
]

controls_binomial <- final_results

rm(
  coef_table,
  ci,
  results,
  predictor_labels,
  row_order,
  stat_cols, 
  final_results
)

controls_binomial
```

###### 💾controls_binomial_table

```{r}
save_output_to_workbook(wb, "Control Variables", controls_binomial)
```

### likelihood

```{r}
# confint(
#   model_controls,
#   parm = "beta_",
#   method = "profile"
# )
```

### interpretation

Only sex and need for cognition were significant. Therefore, only these two control variables are kept in the full model.

## full model —————————————-

### create form

```{r}
#  This first part is only writing out the variables so that when I run the model it is easier to see the options in the model
form_binom <- ItemResponse ~ # ItemResponse is if the participant chose share or not share
  structure_number01 *
  motivation_number01 *
  InfoDistribution *
  InfoImportance +
  sex + # Only sex and NFC contributed to the model and were retained
  NeedCog_Mean +
  (1 | ResponseId) + # These are random intercepts to account for the participant's repeated responses to multiple clues and repeated answering across participants to the clues themselves
  (1 | ItemID)
```

### model

```{r}
# This second part is running the model
model_binom <- glmmTMB( # The package being used is glmmTMB
  form_binom, # This is the form that was created in the first step above
  family = binomial(link = "logit"), # Selects binomial distribution using logit link
  data = dat_long
)

summary(model_binom)
```

#### convergence

Did it run successfully?

```{r}
# The model output shows estimates and random effects without an obvious convergence warning
# TRUE = passes convergence check
model_binom$sdr$pdHess
```

```{r}
saveRDS(model_binom, 
        file = file.path("../artifacts/model_binom.rds")
        )
```

#### dispersion

Dispersion does not appear to be an issue in the model.

```{r}
model_binom_sim_res <- simulateResiduals(
  fittedModel = model_binom
)

plot(model_binom_sim_res)
```

```{r}
# Test dispersion
model_binom_dispersion <- testDispersion(
  model_binom_sim_res
)

model_binom_dispersion
```

```{r}
save_figure_to_workbook(
  wb = wb,
  sheet_name = "Binomial Res",
  figure_file = "../artifacts/fig_binomial_sim_res.png",
  plot_fun = function() plot(model_binom_sim_res),
  width = 10,
  height = 6,
  dpi = 300
)
```

Dispersion does not appear to be an issue due to non-significance in the test.

-   **Dispersion test:** dispersion = 1.0081, *p* = .776, so there is no evidence of overdispersion.

<!-- -->

-   **KS test:** *p* = .32279, so the simulated residual distribution does not show a significant departure from what the model expects.

<!-- -->

-   **Outlier test:** *p* = .3351, so there is no evidence of an unusual number of outliers.

<!-- -->

-   The residual-versus-predicted panel explicitly says **“No significant problems detected.”**

### table

```{r}
#| include: false
rownames(summary(model_binom)$coefficients$cond)
```

```{r}
coef_table <- summary(model_binom)$coefficients$cond
ci <- confint(model_binom, parm = "beta_")

results <- data.frame(
  Predictor = rownames(coef_table),
  b = coef_table[, "Estimate"],
  SE = coef_table[, "Std. Error"],
  Wald_chisq = coef_table[, "z value"]^2,
  p = coef_table[, "Pr(>|z|)"],
  OR = exp(coef_table[, "Estimate"]),
  CI_lower = exp(ci[, 1]),
  CI_upper = exp(ci[, 2]),
  row.names = NULL
)

predictor_labels <- c(
  "(Intercept)" = "Intercept",

  "sex" =
    "Sex (1 = female)",

  "NeedCog_Mean" =
    "Need for Cognition",

  "structure_number01Intergroup" =
    "Interindividual (0) vs. Intergroup (1)",

  "motivation_number01Prosocial" =
    "Proself (0) vs. Prosocial (1)",

  "InfoDistributionUnique" =
    "Common (0) vs. Unique (1)",

  "InfoImportanceHigh Importance" =
    "Low (0) vs. High (1)",

  "structure_number01Intergroup:motivation_number01Prosocial" =
    "Structure × Motivation",

  "structure_number01Intergroup:InfoDistributionUnique" =
    "Structure × Distribution",

  "motivation_number01Prosocial:InfoDistributionUnique" =
    "Motivation × Distribution",

  "structure_number01Intergroup:InfoImportanceHigh Importance" =
    "Structure × Importance",

  "motivation_number01Prosocial:InfoImportanceHigh Importance" =
    "Motivation × Importance",

  "InfoDistributionUnique:InfoImportanceHigh Importance" =
    "Distribution × Importance",

  "structure_number01Intergroup:motivation_number01Prosocial:InfoDistributionUnique" =
    "Structure × Motivation × Distribution",

  "structure_number01Intergroup:motivation_number01Prosocial:InfoImportanceHigh Importance" =
    "Structure × Motivation × Importance",

  "structure_number01Intergroup:InfoDistributionUnique:InfoImportanceHigh Importance" =
    "Structure × Distribution × Importance",

  "motivation_number01Prosocial:InfoDistributionUnique:InfoImportanceHigh Importance" =
    "Motivation × Distribution × Importance",

  "structure_number01Intergroup:motivation_number01Prosocial:InfoDistributionUnique:InfoImportanceHigh Importance" =
    "Structure × Motivation × Distribution × Importance"
)

results$Predictor <- predictor_labels[results$Predictor]

add_section <- function(label, template) {
  row <- template[1, ]
  row[] <- NA
  row$Predictor <- label
  row
}

results <- rbind(
  results,
  add_section("Control Variables", results),
  add_section("Between Manipulations", results),
  add_section("Within Manipulations", results),
  add_section("Interactions", results)
)

row_order <- c(
  "Intercept",

  "Control Variables",
  "Sex (1 = female)",
  "Need for Cognition",

  "Between Manipulations",
  "Interindividual (0) vs. Intergroup (1)",
  "Proself (0) vs. Prosocial (1)",

  "Within Manipulations",
  "Common (0) vs. Unique (1)",
  "Low (0) vs. High (1)",

  "Interactions",
  "Structure × Motivation",
  "Structure × Distribution",
  "Motivation × Distribution",
  "Structure × Importance",
  "Motivation × Importance",
  "Distribution × Importance",
  "Structure × Motivation × Distribution",
  "Structure × Motivation × Importance",
  "Structure × Distribution × Importance",
  "Motivation × Distribution × Importance",
  "Structure × Motivation × Distribution × Importance"
)

final_model_results <- results[
  match(row_order, results$Predictor),
]

rownames(final_model_results) <- NULL

stat_cols <- c(
  "b",
  "SE",
  "Wald_chisq",
  "OR",
  "CI_lower",
  "CI_upper"
)

final_model_results[stat_cols] <-
  lapply(final_model_results[stat_cols], format_stat)

final_model_results$p <-
  format_stat(final_model_results$p, p_value = TRUE)

final_model_results$`OR [95% CI]` <- with(
  final_model_results,
  ifelse(
    OR == "",
    "",
    paste0(OR, " [", CI_lower, ", ", CI_upper, "]")
  )
)

final_model_results <- final_model_results[
  , !names(final_model_results) %in%
    c("OR", "CI_lower", "CI_upper")
]

model_binomial_table <- final_model_results
model_binomial_table
```

###### 💾model_binomial_table

```{r}
save_output_to_workbook(wb, "Binomial Table", model_binomial_table)
```

## joint_test() —————————————-

overall main effects and interactions

similar to Type III ANOVA-style table

#### full

Output should be similar to the binomial regression.

```{r}
joint_results <- joint_tests(model_binom)

joint_results
```

#### decomposition by info I & D

Additional breakdown by information importance and information distribution. This checks which of the combinations of information characteristics has something interesting happening.

Which effects are statistically significant within each information condition?

```{r}
joint_panels <- joint_tests(
  model_binom,
  by = c("InfoImportance", "InfoDistribution")
)

joint_panels
```

```{r}
joint_panels_table <- as.data.frame(joint_panels) %>%
  filter(
    `model term` %in% c(
      "structure_number01",
      "motivation_number01",
      "structure_number01:motivation_number01"
    )
  ) %>%
  mutate(
    Effect = case_when(
      `model term` == "structure_number01" ~ "Structure",
      `model term` == "motivation_number01" ~ "Motivation",
      `model term` == "structure_number01:motivation_number01" ~
        "Structure × Motivation"
    ),

    Chisq_formatted = format_stat(Chisq),

    p_formatted = format_stat(
      p.value,
      p_value = TRUE
    ),

    result = paste0(
      Chisq_formatted,
      " (",
      p_formatted,
      ")"
    ),

    `Information condition` = paste(
      gsub(" Importance", "", InfoImportance),
      InfoDistribution,
      sep = " , "
    )
  ) %>%
  select(
    `Information condition`,
    Effect,
    result
  ) %>%
  pivot_wider(
    names_from = Effect,
    values_from = result
  )

names(joint_panels_table)[
  names(joint_panels_table) == "Structure"
] <- "Structure χ² (p)"

names(joint_panels_table)[
  names(joint_panels_table) == "Motivation"
] <- "Motivation χ² (p)"

names(joint_panels_table)[
  names(joint_panels_table) == "Structure × Motivation"
] <- "Structure × Motivation χ² (p)"

joint_panels_table
```

| Information condition | Structure | Motivation | Structure × Motivation | What it means |
|---------------|---------------|---------------|---------------|---------------|
| **High, Common** | .869 | **\< .001** | **\< .001** | The effect of structure depends on motivation. Unpack with simple interactions. |
| **High, Unique** | **.004** | **\< .001** | .246 | Structure and motivation both have significant effects, with [no]{.underline} evidence that their effects depend on one another. |
| **Low, Common** | .273 | .185 | .110 | [No]{.underline} significant effects of structure, motivation, or their interaction. |
| **Low, Unique** | .618 | .051 | .210 | [No]{.underline} significant effects at the conventional .05 level. Motivation is close, but does not reach significance. |

```{r}
save_output_to_workbook(
  wb, 
  sheet_name = "Joint Panels", 
  output = joint_panels
)

save_output_to_workbook(
  wb, 
  "Joint Panels Table",
  joint_panels_table
)
```

## emmeans() —————————————-

<https://rvlenth.github.io/emmeans/>

The purpose of this analysis is to break down the four-way interaction to understand what is happening with each of the variables.

Because `emmeans` with logistic models often reports contrasts as **odds ratios**, this will usually pair with the predicted probabilities from the bar chart.

These are means that are from the model, which means that they have all of the other predictor variables that were included in the model as well.

Also, random note about the package: the model was built with glmmTMB, so emmeans is relying on methods supplied by glmmTMB to tell it how to use the model data, fixed effects, covariance matrix, etc to compute the estimated marginal means.

<https://rdrr.io/r/stats/coef.html>

`coef()` is a generic function which extracts model coefficients from objects returned by modeling functions. coefficients is an alias for it.

`pairs()` is used on emmeans objects to probe significant effects or interactions

### s \* m

Estimated marginal means for Structure x Motivation across combinations of Distribution x Importance.

```{r}
emm_sm <- emmeans(
  model_binom,
  ~ structure_number01 * motivation_number01 |
    InfoDistribution * InfoImportance,
  type = "response"
)
```

What does sharing look like in each condition?

```{r}
emm_sm_df <- as.data.frame(emm_sm)

emm_sm_df <- emm_sm_df %>%
  mutate(
    `Probability [95% CI]` = sprintf(
      "%.2f [%.2f, %.2f]",
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )

sharing_condition_table <- emm_sm_df %>%
  mutate(
    Condition = paste(
      InfoDistribution,
      gsub(" Importance", "", InfoImportance),
      sep = ", "
    ),
    Group = paste(
      structure_number01,
      motivation_number01
    )
  ) %>%
  select(
    Condition,
    Group,
    `Probability [95% CI]`
  ) %>%
  tidyr::pivot_wider(
    names_from = Group,
    values_from = `Probability [95% CI]`
  )  %>%
  select(
    Condition,
    `Interindividual Prosocial`,
    `Interindividual Proself`,
    `Intergroup Prosocial`,
    `Intergroup Proself`
  )


sharing_condition_table
```

###### 💾sharing_condition_table

```{r}
save_output_to_workbook(
  wb, 
  "Emmeans x Condition", 
  sharing_condition_table
)
```

#### pairs()

Six pairwise comparisons within each information combination.

Limited interpretation

```{r}
pairs(
  emm_sm, 
  adjust = "holm"
  )
```

###### 💾 contrasts_emm_sm

```{r}
save_output_to_workbook(
  wb, 
  sheet_name = "SM Pairs", 
  output = 
    pairs(
      emm_sm, 
      adjust = "holm"
      )
    )

```

#### 📊fig_emm_sm

```{r}
emm_sm_df <- as.data.frame(emm_sm)
```

```{r}
save_output_to_workbook(wb, "SM emmean", emm_sm_df)
```

```{r}
fig_emm_sm <- ggplot(
  emm_sm_df,
  aes(
    x = structure_number01,
    y = prob,
    fill = motivation_number01
  )
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    alpha = 0.5,
    color = "black",
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(
      ymin = asymp.LCL, # 95% CI
      ymax = asymp.UCL
    ),
    position = position_dodge(width = 0.8),
    width = 0.25,
    linewidth = 0.8
  ) +
  facet_grid(
    InfoDistribution ~ InfoImportance
  ) +
  scale_y_continuous(
    breaks = seq(0, 1, 0.2)
  ) +
  coord_cartesian(
    ylim = c(0, 1)
  ) +
  theme_apa() +
  theme(
    text = element_text(
      size = 12,
      family = "serif",
      color = "black"
    ),

    axis.title = element_text(
      size = 12,
      face = "plain",
      color = "black"
    ),

    axis.text = element_text(
      size = 11,
      face = "plain",
      color = "black"
    ),

    strip.text = element_text(
      size = 12,
      face = "plain",
      family = "serif"
    ),

    legend.title = element_text(
      size = 12,
      face = "plain"
    ),

    legend.text = element_text(
      size = 11,
      face = "plain"
    ),

    axis.ticks = element_line(
      color = "black",
      linewidth = 0.5
    ),

    axis.ticks.length = unit(0.10, "cm"),

    axis.line = element_line(
      color = "black"
    ),

    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),

    panel.spacing = unit(0.8, "lines")
  ) +
  labs(
    x = "Structure",
    y = "Predicted Probability of Sharing",
    fill = "Motivation"
  ) +
  scale_fill_manual(
    name = "Motivation",
    values = c(
      "Proself" = "#0C7BDC",
      "Prosocial" = "#FFC20A"
    )
  )

fig_emm_sm
```

###### 💾 fig_emm_sm

```{r}
save_figure_to_workbook(
  wb = wb,
  sheet_name = "SM Figure",
  figure_file = "../figures/SM_Interaction.png",
  plot_obj = fig_emm_sm,
  width = 8,
  height = 6,
  dpi = 300
)
```

## significant panels —————————-

Explore the significant panels

-   High/Common

-   High/Unique

### high & common

both sets of simple effects because both Structure x Motivation is significant

```{r}
emm_high_common <- emmeans(
  model_binom,
  ~ structure_number01 * motivation_number01, # note *
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Common"
  ),
  type = "response"
)

emm_high_common

pairs(emm_high_common)
```

```{r}
save_output_to_workbook(
  wb,
  "HC emmeans",
  as.data.frame(emm_high_common)
)

save_output_to_workbook(
  wb,
  "HC Pairs",
  as.data.frame(pairs(emm_high_common))
)
```

#### compare Structure within each Motivation

-   Does Structure matter among Proself participants?

-   Does Structure matter among Prosocial participants?

```{r}
hc_structure <- emmeans(
  model_binom,
  ~ structure_number01 | motivation_number01, # note order and |
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Common"
  ),
  type = "response"
)

hc_structure

pairs(hc_structure)
```

```{r}
save_output_to_workbook(
  wb,
  "HC Structure Emmeans",
  hc_structure
)

save_output_to_workbook(
  wb,
  "HC Structure Pairs",
  as.data.frame(pairs(hc_structure))
)
```

#### compare Motivation within each Structure

-   Does Motivation matter in the Interindividual condition?

<!-- -->

-   Does Motivation matter in the Intergroup condition?

```{r}
hc_motivation <- emmeans(
  model_binom,
  ~ motivation_number01 | structure_number01,  # note order and |
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Common"
  ),
  type = "response"
)

hc_motivation

pairs(hc_motivation)
```

```{r}
save_output_to_workbook(
  wb,
  "HC Motivation Emmeans",
  hc_motivation
)

save_output_to_workbook(
  wb,
  "HC Motivation Pairs",
  as.data.frame(pairs(hc_motivation))
)
```

### high & unique

no significant structure x motivation interaction, but reason to look more closely at the prosocial/intergroup

structure was significant -\> further investigation

motivation was significant -\> further investigation

#### Structure

Across Motivation conditions, do Interindividual and Intergroup differ for High/Unique information?

```{r}
hu_structure_overall <- emmeans(
  model_binom,
  ~ structure_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

hu_structure_overall

pairs(hu_structure_overall)
```

```{r}
save_output_to_workbook(
  wb,
  "HU Structure Overall",
  hu_structure_overall
)

save_output_to_workbook(
  wb,
  "HU Structure Pairs",
  as.data.frame(pairs(hu_structure_overall))
)
```

#### Structure \| Motivation

Based on the visualization, prosocials seemed to be sharing less in the intergroup condition than in the interindividual condition. This is a check of that.

Among Prosocial participants, is sharing lower in the Intergroup condition than in the Interindividual condition?

Among prosocial participants, is the intergroup different from the interindividual? (And also, among the proself participants, is the intergroup different from the interindividual?)

Yes, there is a significant different among Prosocial participants. (simple effect of structure?)

Among prosocial participants, the predicted probability of sharing high-importance, unique information was significantly higher in the interindividual condition (.722) than in the intergroup condition (.445), OR = 3.24, p = .003.

```{r}
hu_structure <- emmeans(
  model_binom,
  ~ structure_number01 | motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

hu_structure

pairs(hu_structure)
```

```{r}
save_output_to_workbook(
  wb,
  "HU S|M Emmeans",
  as.data.frame(hu_structure)
)

save_output_to_workbook(
  wb,
  "HU S|M Pairs",
  as.data.frame(pairs(hu_structure))
)
```

#### Motivation

Across Structure conditions, do Proself and Prosocial differ for High/Unique information?

```{r}
hu_motivation_overall <- emmeans(
  model_binom,
  ~ motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

hu_motivation_overall

pairs(hu_motivation_overall)
```

```{r}
save_output_to_workbook(
  wb,
  "HU Motivation Emmeans",
  as.data.frame(hu_motivation_overall)
)

save_output_to_workbook(
  wb,
  "HU Motivation Pairs",
  as.data.frame(pairs(hu_motivation_overall))
)
```

#### Motivation \| Structure

Within the Intergroup condition, do Prosocial participants differ from Proself participants?

```{r}
hu_motivation <- emmeans(
  model_binom,
  ~ motivation_number01 | structure_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

hu_motivation

pairs(hu_motivation)
```

```{r}
save_output_to_workbook(
  wb,
  "HU M|S Emmeans",
  as.data.frame(hu_motivation)
)

save_output_to_workbook(
  wb,
  "HU M|S Pairs",
  as.data.frame(pairs(hu_motivation))
)
```

#### Motivation \* Structure

```{r}
hu_cells <- emmeans(
  model_binom,
  ~ structure_number01 * motivation_number01,
  at = list(
    InfoImportance = "High Importance",
    InfoDistribution = "Unique"
  ),
  type = "response"
)

hu_cells
```

### Build table

#### high Importance Common

first check

```{r}
names(as.data.frame(
  summary(
    pairs(hc_structure),
    type = "response",
    infer = TRUE
  )
))
```

##### structure

```{r}
hc_structure_df <- as.data.frame(hc_structure) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )

hc_structure_pairs <- as.data.frame(
  summary(
    pairs(hc_structure, adjust = "holm"),
    type = "response",
    infer = TRUE
  )
) %>%
  mutate(
    OR_CI = format_or_ci(
      odds.ratio,
      asymp.LCL,
      asymp.UCL
    ),
    p_display = format_p_value(p.value)
  )
```

##### motivation

```{r}
hc_motivation_df <- as.data.frame(hc_motivation) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )

hc_motivation_pairs <- as.data.frame(
  summary(
    pairs(hc_motivation, adjust = "holm"),
    type = "response",
    infer = TRUE
  )
) %>%
  mutate(
    OR_CI = format_or_ci(
      odds.ratio,
      asymp.LCL,
      asymp.UCL
    ),
    p_display = format_p_value(p.value)
  )
```

##### table combine

```{r}
table_hc <- tribble(
  ~Comparison, ~`P [95% CI]`, ~`OR [95% CI]`, ~p,

  "Proself", "", "", "",

  "  Interindividual",
  hc_structure_df$P_CI[
    hc_structure_df$structure_number01 == "Interindividual" &
    hc_structure_df$motivation_number01 == "Proself"
  ],
  "", "",

  "  Intergroup",
  hc_structure_df$P_CI[
    hc_structure_df$structure_number01 == "Intergroup" &
    hc_structure_df$motivation_number01 == "Proself"
  ],
  "", "",

  "  Interindividual vs. Intergroup",
  "",
  hc_structure_pairs$OR_CI[
    hc_structure_pairs$motivation_number01 == "Proself"
  ],
  hc_structure_pairs$p_display[
    hc_structure_pairs$motivation_number01 == "Proself"
  ],

  "Prosocial", "", "", "",

  "  Interindividual",
  hc_structure_df$P_CI[
    hc_structure_df$structure_number01 == "Interindividual" &
    hc_structure_df$motivation_number01 == "Prosocial"
  ],
  "", "",

  "  Intergroup",
  hc_structure_df$P_CI[
    hc_structure_df$structure_number01 == "Intergroup" &
    hc_structure_df$motivation_number01 == "Prosocial"
  ],
  "", "",

  "  Interindividual vs. Intergroup",
  "",
  hc_structure_pairs$OR_CI[
    hc_structure_pairs$motivation_number01 == "Prosocial"
  ],
  hc_structure_pairs$p_display[
    hc_structure_pairs$motivation_number01 == "Prosocial"
  ],

  "Interindividual", "", "", "",

  "  Proself",
  hc_motivation_df$P_CI[
    hc_motivation_df$structure_number01 == "Interindividual" &
    hc_motivation_df$motivation_number01 == "Proself"
  ],
  "", "",

  "  Prosocial",
  hc_motivation_df$P_CI[
    hc_motivation_df$structure_number01 == "Interindividual" &
    hc_motivation_df$motivation_number01 == "Prosocial"
  ],
  "", "",

  "  Proself vs. Prosocial",
  "",
  hc_motivation_pairs$OR_CI[
    hc_motivation_pairs$structure_number01 == "Interindividual"
  ],
  hc_motivation_pairs$p_display[
    hc_motivation_pairs$structure_number01 == "Interindividual"
  ],

  "Intergroup", "", "", "",

  "  Proself",
  hc_motivation_df$P_CI[
    hc_motivation_df$structure_number01 == "Intergroup" &
    hc_motivation_df$motivation_number01 == "Proself"
  ],
  "", "",

  "  Prosocial",
  hc_motivation_df$P_CI[
    hc_motivation_df$structure_number01 == "Intergroup" &
    hc_motivation_df$motivation_number01 == "Prosocial"
  ],
  "", "",

  "  Proself vs. Prosocial",
  "",
  hc_motivation_pairs$OR_CI[
    hc_motivation_pairs$structure_number01 == "Intergroup"
  ],
  hc_motivation_pairs$p_display[
    hc_motivation_pairs$structure_number01 == "Intergroup"
  ]
)

table_hc
```

#### high importance, unique

```{r}
hu_structure_df <- as.data.frame(hu_structure_overall) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )

hu_structure_pairs <- as.data.frame(
  summary(
    pairs(hu_structure_overall, adjust = "holm"),
    type = "response",
    infer = TRUE
  )
) %>%
  mutate(
    OR_CI = format_or_ci(
      odds.ratio,
      asymp.LCL,
      asymp.UCL
    ),
    p_display = format_p_value(p.value)
  )
```

##### motivation

```{r}
hu_motivation_df <- as.data.frame(hu_motivation_overall) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )

hu_motivation_pairs <- as.data.frame(
  summary(
    pairs(hu_motivation_overall, adjust = "holm"),
    type = "response",
    infer = TRUE
  )
) %>%
  mutate(
    OR_CI = format_or_ci(
      odds.ratio,
      asymp.LCL,
      asymp.UCL
    ),
    p_display = format_p_value(p.value)
  )
```

#### table combine

```{r}
table_hu <- tribble(
  ~Comparison, ~`P [95% CI]`, ~`OR [95% CI]`, ~p,

  "Structure", "", "", "",

  "  Interindividual",
  hu_structure_df$P_CI[
    hu_structure_df$structure_number01 == "Interindividual"
  ],
  "", "",

  "  Intergroup",
  hu_structure_df$P_CI[
    hu_structure_df$structure_number01 == "Intergroup"
  ],
  "", "",

  "  Interindividual vs. Intergroup",
  "",
  hu_structure_pairs$OR_CI[1],
  hu_structure_pairs$p_display[1],

  "Motivation", "", "", "",

  "  Proself",
  hu_motivation_df$P_CI[
    hu_motivation_df$motivation_number01 == "Proself"
  ],
  "", "",

  "  Prosocial",
  hu_motivation_df$P_CI[
    hu_motivation_df$motivation_number01 == "Prosocial"
  ],
  "", "",

  "  Proself vs. Prosocial",
  "",
  hu_motivation_pairs$OR_CI[1],
  hu_motivation_pairs$p_display[1]
)

table_hu
```

#### save tables

```{r}
save_output_to_workbook(
  wb,
  "HC Follow-up Table",
  table_hc
)

save_output_to_workbook(
  wb,
  "HU Follow-up Table",
  table_hu
)
```

### Build table

#### dataframes

```{r}
hc_probability_df <- as.data.frame(hc_structure) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )
```

```{r}
hu_probability_df <- as.data.frame(hu_cells) %>%
  mutate(
    P_CI = format_p_ci(
      prob,
      asymp.LCL,
      asymp.UCL
    )
  )
```

```{r}
table_high_probabilities <- tribble(
  ~`Information Distribution`,
  ~Motivation,
  ~Interindividual,
  ~Intergroup,

  "Common",
  "Proself",
  hc_probability_df$P_CI[
    hc_probability_df$structure_number01 == "Interindividual" &
    hc_probability_df$motivation_number01 == "Proself"
  ],
  hc_probability_df$P_CI[
    hc_probability_df$structure_number01 == "Intergroup" &
    hc_probability_df$motivation_number01 == "Proself"
  ],

  "",
  "Prosocial",
  hc_probability_df$P_CI[
    hc_probability_df$structure_number01 == "Interindividual" &
    hc_probability_df$motivation_number01 == "Prosocial"
  ],
  hc_probability_df$P_CI[
    hc_probability_df$structure_number01 == "Intergroup" &
    hc_probability_df$motivation_number01 == "Prosocial"
  ],

  "Unique",
  "Proself",
  hu_probability_df$P_CI[
    hu_probability_df$structure_number01 == "Interindividual" &
    hu_probability_df$motivation_number01 == "Proself"
  ],
  hu_probability_df$P_CI[
    hu_probability_df$structure_number01 == "Intergroup" &
    hu_probability_df$motivation_number01 == "Proself"
  ],

  "",
  "Prosocial",
  hu_probability_df$P_CI[
    hu_probability_df$structure_number01 == "Interindividual" &
    hu_probability_df$motivation_number01 == "Prosocial"
  ],
  hu_probability_df$P_CI[
    hu_probability_df$structure_number01 == "Intergroup" &
    hu_probability_df$motivation_number01 == "Prosocial"
  ]
)

table_high_probabilities
```

#### save table

```{r}
save_output_to_workbook(
  wb,
  "High Importance Probabilities",
  table_high_probabilities
)
```

### Build table 

#### dataframes

```{r}
hu_structure_pairs <- as.data.frame(
  summary(
    pairs(hu_structure, adjust = "holm"),
    type = "response",
    infer = TRUE
  )
) %>%
  mutate(
    OR_CI = format_or_ci(
      odds.ratio,
      asymp.LCL,
      asymp.UCL
    ),
    p_display = format_p_value(p.value)
  )
```

```{r}
hu_motivation_pairs <- as.data.frame(
  summary(
    pairs(hu_motivation, adjust = "holm"),
    type = "response",
    infer = TRUE
  )
) %>%
  mutate(
    OR_CI = format_or_ci(
      odds.ratio,
      asymp.LCL,
      asymp.UCL
    ),
    p_display = format_p_value(p.value)
  )
```

```{r}
table_high_pairs <- tribble(
  ~Comparison, ~`OR [95% CI]`, ~p,

  "Common", "", "",

  "  Proself: Interindividual vs. Intergroup",
  hc_structure_pairs$OR_CI[
    hc_structure_pairs$motivation_number01 == "Proself"
  ],
  hc_structure_pairs$p_display[
    hc_structure_pairs$motivation_number01 == "Proself"
  ],

  "  Prosocial: Interindividual vs. Intergroup",
  hc_structure_pairs$OR_CI[
    hc_structure_pairs$motivation_number01 == "Prosocial"
  ],
  hc_structure_pairs$p_display[
    hc_structure_pairs$motivation_number01 == "Prosocial"
  ],

  "  Interindividual: Proself vs. Prosocial",
  hc_motivation_pairs$OR_CI[
    hc_motivation_pairs$structure_number01 == "Interindividual"
  ],
  hc_motivation_pairs$p_display[
    hc_motivation_pairs$structure_number01 == "Interindividual"
  ],

  "  Intergroup: Proself vs. Prosocial",
  hc_motivation_pairs$OR_CI[
    hc_motivation_pairs$structure_number01 == "Intergroup"
  ],
  hc_motivation_pairs$p_display[
    hc_motivation_pairs$structure_number01 == "Intergroup"
  ],

  "Unique", "", "",

  "  Proself: Interindividual vs. Intergroup",
  hu_structure_pairs$OR_CI[
    hu_structure_pairs$motivation_number01 == "Proself"
  ],
  hu_structure_pairs$p_display[
    hu_structure_pairs$motivation_number01 == "Proself"
  ],

  "  Prosocial: Interindividual vs. Intergroup",
  hu_structure_pairs$OR_CI[
    hu_structure_pairs$motivation_number01 == "Prosocial"
  ],
  hu_structure_pairs$p_display[
    hu_structure_pairs$motivation_number01 == "Prosocial"
  ],

  "  Interindividual: Proself vs. Prosocial",
  hu_motivation_pairs$OR_CI[
    hu_motivation_pairs$structure_number01 == "Interindividual"
  ],
  hu_motivation_pairs$p_display[
    hu_motivation_pairs$structure_number01 == "Interindividual"
  ],

  "  Intergroup: Proself vs. Prosocial",
  hu_motivation_pairs$OR_CI[
    hu_motivation_pairs$structure_number01 == "Intergroup"
  ],
  hu_motivation_pairs$p_display[
    hu_motivation_pairs$structure_number01 == "Intergroup"
  ]
)

table_high_pairs
```

#### save table

```{r}
save_output_to_workbook(
  wb,
  "High Importance Pairwise",
  table_high_pairs
)
```

## Save wb to excel —————————————-

```{r}
data.frame(
  Sheet = seq_along(names(wb)),
  Worksheet = names(wb)
)
```

```{r}
#| warning: false

cat("Formatting worksheets...\n")

for (sheet in names(wb)) {
  
  cat("Formatting:", sheet, "\n")
  
  setColWidths(
    wb,
    sheet = sheet,
    cols = 1:30,
    widths = "auto"
  )
}

cat("Finished formatting worksheets.\n")
cat("Saving workbook...\n")

saveWorkbook(
  wb,
  excel_export_file_location,
  overwrite = TRUE
)

cat("Workbook saved successfully.\n")
```

## End —————————————-

```{r}
print("end of script")
```
