---
title: "cooperation"
format: html
---

```{r}
filtered_data <- readRDS("../artifacts/filtered_data.rds")
codebook <- readRDS("../artifacts/codebook.rds")
source("../_common.R")
```

```{r}
#| message: false
#| warning: false
library(lsr)
library(emmeans)
library(yarrr)
library(ggplot2)
library(car)
library(dplyr)
```

## 2. SELF-REPORT STATE COOPERATION

##### 📊 Fig: Cooperation

```{r}
figure_density_motivation <- ggplot(filtered_data, aes(x = Manipulation_Mean)) +
  geom_density(alpha = 0.4) +  # transparent overlap
  theme_classic() +
  theme(
    text = element_text(size = 16, family = "serif"),
    axis.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold"),
    axis.ticks = element_line(color = "black", size = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  ) +
  labs(
    x = "Competition Scores",
    y = "Density",
    fill = "Motivation"
  )

print(figure_density_motivation)
```

##### 📊 Fig: Reward Conditions Only

```{r}
figure_manipulation_check <- ggplot(filtered_data, aes(x = motivation, y = Manipulation_Mean)) +
  geom_boxplot(outlier.shape = NA) +  # Removes default outliers
  geom_jitter(width = 0.2, alpha = 0.5, color = "blue") +
  theme_classic()+
  theme(
    text = element_text(size = 16, family = "serif"),
    axis.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold"),
    
    # ✅ These lines control the TICK MARKS
    axis.ticks = element_line(color = "black", size = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    
    # ✅ These restore AXIS LINES that ticks sit on
    axis.line = element_line(color = "black"),
    
    # ✅ Remove background gridlines (APA prefers a clean look)
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  )+
    labs(
    x = "Reward",
    y = "Competition Scores"
  )

print(figure_manipulation_check)
```

```{r}
ggsave(
  "../figures/figure_manipulation_check.png", 
  plot = figure_manipulation_check, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

##### 📊 Fig: Reward & Structure

```{r}
figure_violin_by_structure <- ggplot(
  filtered_data,
  aes(x = motivation, y = Manipulation_Mean, fill = motivation)
) +
  geom_violin(trim = FALSE, alpha = 0.4) +
  geom_boxplot(width = 0.12, outlier.shape = NA) +
  facet_wrap(~ structure) +
  theme_classic() +
  theme(
    text = element_text(size = 16, family = "serif"),
    axis.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold"),
    axis.ticks = element_line(color = "black", size = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    legend.position = "none"
  ) +
  labs(x = "Motivation", y = "Competition Scores")

print(figure_violin_by_structure)
```

### Assumptions

##### DV

```{r}
# Histogram
hist(filtered_data$Manipulation_Mean, main = "Histogram of DV", xlab = "DV")

# Density plot
plot(density(filtered_data$Manipulation_Mean, na.rm = TRUE), main = "Density of DV")

# Boxplot
boxplot(filtered_data$Manipulation_Mean, main = "Boxplot of DV")

```

distribution appears to be reasonably distributed

##### multicollinearity

```{r}
m <- glm(Manipulation_Mean ~ Q14.1 + sex + SES_mean + hispanic +
           NeedCog_Mean + 
           DirtyDozen_Narcissism +
           DirtyDozen_Psychopathy +
           DirtyDozen_Machiavellianism +
           SVO_angle, 
         data = filtered_data, 
         family = gaussian(link = "identity"))

vif(m)
```

Rule of thumb: VIF \> 5 (some say 10) indicates problematic collinearity.

Only slight tiny issue, but all okay.

##### 📊 Fig: Manipulation_Mean

check all of the control variables with the state measure, with within participants variable.

```{r}
# Check variable

# Histogram
hist(filtered_data$Manipulation_Mean, main = "Distribution of Outcome", xlab = "Outcome Variable")

# Density plot
plot(density(filtered_data$Manipulation_Mean, na.rm = TRUE))

# Q-Q plot
qqnorm(filtered_data$Manipulation_Mean)
qqline(filtered_data$Manipulation_Mean)

# Descriptive stats
describe(filtered_data$Manipulation_Mean)
```

## linear regression

### ✅ control variables

```{r}
# Test of the controls

# Basic linear regression
state_model_controls <- lm(Manipulation_Mean ~ 
  Q14.1 + sex + SES_mean + hispanic +
  NeedCog_Mean + DirtyDozen_Narcissism +
  DirtyDozen_Psychopathy + DirtyDozen_Machiavellianism +
  SVO_angle, data = filtered_data)

# Summary of results
summary(state_model_controls)
```

```{r}
nobs(state_model_controls)
```

```{r}
confint(state_model_controls, level = 0.95)
```

###### assumptions

```{r}
model <- state_model_controls
```

###### linearity

-   The residuals should scatter randomly around the horizontal line (0).

-   If you see curves or systematic patterns, the relationship may not be linear.

```{r}
#| message: false
#| warning: false

# Partial residual plots
car::crPlots(model)

# Or a scatterplot of residuals vs. fitted values
plot(model, which = 1)  # Residuals vs Fitted
```

###### homoscedasticity (equal variance of errors)

-   In the plot, points should form a horizontal band (not a funnel shape).

-   For the Breusch–Pagan test, *p* \> .05 means homoscedasticity (good).

```{r}
plot(model, which = 3)  # Scale-Location plot
lmtest::bptest(model)   # Breusch-Pagan test
```

###### normality of errors

-   In the Q–Q plot, points should roughly follow the diagonal line.

-   Shapiro–Wilk test: *p* \> .05 means residuals are approximately normal.

```{r}
plot(model, which = 2)    # Q-Q plot
shapiro.test(residuals(model))
```

###### no multicollinearity

-   VIF \< 5 → acceptable (some use \< 10 as a lenient rule)

-   Tolerance (1/VIF) \> 0.2 → acceptable

-   If a variable has a high VIF, consider removing or combining correlated predictors.

```{r}
car::vif(model)
```

control variables that say based on this would be:

-   Machiavellianism

### ✅ full model

```{r}
# Test of the controls

# Basic linear regression
state_model <- lm(Manipulation_Mean ~ (structure_number01 * motivation_number01) +
  DirtyDozen_Machiavellianism,
  data = filtered_data)

# Summary of results
summary(state_model)
```

###### cook's

```{r}
# Compute Cook's distance
cooks_d <- cooks.distance(state_model)

# Common cutoff
cutoff <- 4 / nrow(filtered_data)

which(cooks_d > cutoff)

filtered_data %>%
  dplyr::mutate(CooksD = cooks_d) %>%
  dplyr::filter(CooksD > cutoff) %>%
  dplyr::select(ResponseId, CooksD)

plot(cooks_d, pch = 19, main = "Cook's Distance")
abline(h = cutoff, col = "red", lty = 2)
```

###### assumptions

```{r}
model <- state_model
```

###### linearity

-   The residuals should scatter randomly around the horizontal line (0).

-   If you see curves or systematic patterns, the relationship may not be linear.

```{r}
#| message: false
#| warning: false

# Partial residual plots
car::residualPlots(model)

# Or a scatterplot of residuals vs. fitted values
plot(model, which = 1)  # Residuals vs Fitted
```

###### homoscedasticity

-   In the plot, points should form a horizontal band (not a funnel shape).

-   For the Breusch–Pagan test, *p* \> .05 means homoscedasticity (good).

```{r}
plot(model, which = 3)  # Scale-Location plot
lmtest::bptest(model)   # Breusch-Pagan test
```

###### normality of errors

-   In the Q–Q plot, points should roughly follow the diagonal line.

-   Shapiro–Wilk test: *p* \> .05 means residuals are approximately normal.

```{r}
plot(model, which = 2)    # Q-Q plot
shapiro.test(residuals(model))
```

```{r}
plot(model, which = 1)        # Residuals vs Fitted (linearity + variance)
car::qqPlot(model)            # Q-Q plot (tails/skew); better than base
lmtest::bptest(model)         # Breusch–Pagan for heteroskedasticity
```

```{r}
# Identify cases with largest |studentized residuals|
rstud <- rstudent(model)   # studentized residuals
which(abs(rstud) > 2)      # commonly flagged as potential outliers
```

###### no multicollinearity

-   VIF \< 5 → acceptable (some use \< 10 as a lenient rule)

-   Tolerance (1/VIF) \> 0.2 → acceptable

-   If a variable has a high VIF, consider removing or combining correlated predictors.

```{r}
car::vif(model)
```

##### outliers

```{r}
#Update numbers to match the cases flagged above
filtered_data[c(27, 30, 89), ]
```

## GLM

### GLM with 3 dirty dozen

```{r}
state_model_controls_glm <- glm(Manipulation_Mean ~ Q14.1 + sex + SES_mean + hispanic +
      NeedCog_Mean + DirtyDozen_Narcissism +
      DirtyDozen_Psychopathy + DirtyDozen_Machiavellianism +
      SVO_angle,
    data = filtered_data,
    family = gaussian(link = "identity"))

summary(state_model_controls_glm)
```

```{r}
confint(state_model_controls_glm, level = 0.95)
```

Outcome of control check -\> DirtyDozen_Machiavellianism was significant

### GLM with conditions and Machiavellianism

```{r}
state_model_glm <- glm(Manipulation_Mean ~ 
      (structure_number01 * motivation_number01) +
      DirtyDozen_Machiavellianism +
      SVO_angle,
    data = filtered_data,
    family = gaussian(link = "identity"))

summary(state_model_glm)
```

## means by conditions

```{r}
desc_by_cell("Manipulation_Mean")
```

###### 📊 Fig: Manipulation Check

```{r}
figure_manipulation_check_anova <- ggplot(filtered_data, aes(x = structure_rev, y = competition_score, fill = motivation)) +
  geom_boxplot(position = position_dodge(width = 0.75), outlier.shape = NA) +
  geom_jitter(aes(color = motivation), 
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              alpha = 0.5, size = 2, show.legend = FALSE) +
    stat_summary(
    fun = mean,
    geom = "point",
    aes(group = motivation),
    position = position_dodge(width = 0.75),
    shape = 21,           # Filled circle
    size = 3,
    color = "black",
    fill = "white"        # So it stands out on colored boxplots
  ) +
  scale_fill_brewer(palette = "Pastel1") +
  scale_color_brewer(palette = "Set1") +
  theme_classic() +
  theme(
    text = element_text(size = 25, family = "serif"),
    axis.title = element_text(size = 25, face = "bold", color = "black"),
    axis.text = element_text(size = 25, face = "plain", color = "black"),
    axis.ticks = element_line(color = "black", linewidth = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    legend.title = element_text(size = 25, color = "black"),
    legend.text = element_text(size = 25, color = "black")
  ) +
  labs(
    title = "",
    x = "Group Structure",
    y = "Score",
    fill = "Motivation"
  )

print(figure_manipulation_check_anova)
```

```{r}
ggsave(
  "../figures/figure_manipulation_check_anova.png", 
  plot = figure_manipulation_check_anova, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

```{r}
# # pirate plot based on how participants shared information broken out by condition. 
# pirateplot(competition_score ~ condition_rev,
#            data = filtered_data,
#            main = NULL,  
#            xlab = "",
#            ylab = "",
#            pal = "xmen",
#            inf.method = "se",
#            avg.line.fun = mean,
#            theme = 2)

pirateplot(competition_score ~ condition_rev,
           data = filtered_data,
           main = NULL,  
           xlab = "",
           ylab = "",
           yaxt = "n",
           xaxt = "n",
           ylim = c(1, 5),
           gl.col = NA,
           bty = "n",
           pal = "xmen",
           inf.method = "se",
           avg.line.fun = mean,
           theme = 2)

axis(side = 2, at = 1:5, labels = 1:5, las = 1)
box(bty = "l")
```

## ANCOVA test

```{r}
# Only significant included, no trends
# Machiavellianism age sex need for cognition

# Full ANCOVA model
ancova_model <- aov(
  Manipulation_Mean ~ (motivation * structure_rev) +
   DirtyDozen_Machiavellianism,
  data = filtered_data
)

# Type I (sequential) sums of squares
# summary(ancova_model)

# Type III sums of squares (common in ANCOVA reporting)
library(car)
Anova(ancova_model, type = 3)
ancova_typeIII <- Anova(ancova_model, type = 3)
```

#### estimated means

```{r}
library(emmeans)
emmeans(ancova_model, ~ motivation)      # adjusted means by motivation
emmeans(ancova_model, ~ structure_rev)   # adjusted means by structure

```

#### eta-squared

```{r}
library(effectsize)
eta_squared(ancova_typeIII, partial = TRUE)

# Note on the warning: I have approxmately equal group sizes, so Type iii is not an issue
```

motivation, structure, machiavellianism

#### assumptions

```{r}
# Scatterplots of DV vs. covariates
plot(filtered_data$Manipulation_Mean, filtered_data$Q14.1)
plot(filtered_data$Manipulation_Mean, filtered_data$NeedCog_Mean)
plot(filtered_data$Manipulation_Mean, filtered_data$DirtyDozen_Machiavellianism)

# Add regression lines for clarity
library(ggplot2)
ggplot(filtered_data, aes(x = NeedCog_Mean, y = Manipulation_Mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

```

```{r}
# Extract residuals
resid_vals <- residuals(ancova_model)

# Histogram + Q-Q plot
hist(resid_vals)
qqnorm(resid_vals); qqline(resid_vals)

# Shapiro-Wilk test
shapiro.test(resid_vals)  # ns p-value → assumption holds

shapiro.test(residuals(ancova_model))  # Shapiro-Wilk test

# How to interpret:
# 
# Null hypothesis: Residuals are normally distributed.
# 
# ✔️ If p > 0.05: You fail to reject the null → normality is not violated.
# 
# ❌ If p < 0.05: You reject the null → indicates non-normality.
# 
# Note: The Shapiro test is sensitive to large sample sizes. In large samples, slight non-normality may still yield a small p-value — look at the QQ plot too.

```

```{r}
library(car)
leveneTest(Manipulation_Mean ~ motivation * structure_rev, data = filtered_data)

# How to interpret:
# 
# Null hypothesis: Variances are equal across all groups.
# 
# ✔️ If p > 0.05: You fail to reject the null → meaning that we have equal variances → assumption met.

# ❌ If p < 0.05: You reject the null → meaning that we have unequal variances → assumption violated.
#
# If violated, you might:
# 
# Use robust ANOVA methods (e.g., Welch’s ANOVA)
# 
# Use transformation or bootstrapping
# 
# Proceed with caution if your group sizes are roughly equal (ANOVA is robust in that case)
```

###### 🗑️ 📊 Fig: ANCOVA

```{r}
# Hold covariates at their sample means (recommended for clarity)
at_vals <- with(filtered_data, list(
  Q14.1 = mean(Q14.1, na.rm = TRUE),
  sex = mean(sex, na.rm = TRUE),                       # if coded 0/1, this is the sample proportion female=1
  NeedCog_Mean = mean(NeedCog_Mean, na.rm = TRUE),
  DirtyDozen_Machiavellianism = mean(DirtyDozen_Machiavellianism, na.rm = TRUE)
))

emm_int <- emmeans(
  ancova_model,
  ~ motivation * structure_rev,
  at = at_vals
)
emm_df <- as.data.frame(emm_int)

p_emm <- ggplot(emm_df, aes(x = structure_rev, y = emmean,
                            color = motivation, group = motivation)) +
  geom_point(position = position_dodge(width = 0.2), size = 3) +
  geom_line(position = position_dodge(width = 0.2), linewidth = 0.7) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                width = 0.08, position = position_dodge(width = 0.2)) +
  labs(x = "Group structure",
       y = "Adjusted mean cooperation (ANCOVA)",
       color = "Motivation",
       title = "") +
  theme_classic(base_size = 14)

print(p_emm)

```

```{r}
# Adjusted means for motivation (averaged over structure; covariates set at means)
emm_mot <- emmeans(ancova_model, ~ motivation, at = at_vals)
df_mot  <- as.data.frame(emm_mot)

p_mot <- ggplot(df_mot, aes(x = motivation, y = emmean)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.1) +
  labs(x = "Motivation", y = "Adjusted mean cooperation (ANCOVA)", title = "") +
  theme_classic(base_size = 14)

# Adjusted means for structure (averaged over motivation; covariates set at means)
emm_str <- emmeans(ancova_model, ~ structure_rev, at = at_vals)
df_str  <- as.data.frame(emm_str)

p_str <- ggplot(df_str, aes(x = structure_rev, y = emmean)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.1) +
  labs(x = "Group structure", y = "Adjusted mean cooperation (ANCOVA)", title = "") +
  theme_classic(base_size = 14)

# Print either or both:
print(p_mot)
print(p_str)
```

###### 📊 Fig: ANCOVA

```{r}
figure_manipulation_check_anova <- ggplot(filtered_data, aes(x = structure_rev, y = Manipulation_Mean, fill = motivation)) +
  geom_boxplot(position = position_dodge(width = 0.75), outlier.shape = NA) +
  geom_jitter(aes(color = motivation), 
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              alpha = 0.5, size = 2, show.legend = FALSE) +
    stat_summary(
    fun = mean,
    geom = "point",
    aes(group = motivation),
    position = position_dodge(width = 0.75),
    shape = 21,           # Filled circle
    size = 3,
    color = "black",
    fill = "white"        # So it stands out on colored boxplots
  ) +
  scale_fill_brewer(palette = "Pastel1") +
  scale_color_brewer(palette = "Set1") +
    scale_fill_brewer(
    palette = "Pastel1",
    labels = c("proself" = "Proself", "prosocial" = "Prosocial")
  ) +
  scale_color_brewer(
    palette = "Set1",
    labels = c("proself" = "Proself", "prosocial" = "Prosocial")
  ) +
  theme_classic() +
  theme(
    text = element_text(size = 25, family = "serif"),
    axis.title = element_text(size = 25, face = "bold", color = "black"),
    axis.text = element_text(size = 25, face = "plain", color = "black"),
    axis.ticks = element_line(color = "black", linewidth = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    legend.title = element_text(size = 25, color = "black"),
    legend.text = element_text(size = 25, color = "black")
  ) +
  scale_x_discrete(labels = c("MTS" = "Intergroup", 
                            "group" = "Interindividual")) +
  labs(
    title = "",
    x = "Group Structure",
    y = "Cooperation",
    fill = "Motivation"
  )

print(figure_manipulation_check_anova)
```

## END

```{r}
print("Success! All code has been run.")
```
