---
ii---
title: "03_01_05_InfoSharingCOM"
format: html
---

```{r}
gee_long_shared <- readRDS("../artifacts/gee_long_shared.rds")
codebook <- readRDS("../artifacts/codebook.rds")
source("../_common.R")
```

```{r}
library(glmmTMB)
library(DHARMa)
# library(ggpattern)
library(papaja)
```

## ---- INFORMATION SHARING TASK ----

Based on Model Testing, the only significant controls to the model were:

-   Need for Cognition

-   Sex

[Vignette for glmmTMB package](https://cran.r-project.org/web/packages/glmmTMB/vignettes/model_evaluation.pdf)

## Full Model

### Setup

```{r}
#1) Identify the variables in the model
form <- Count ~ (structure_number01 * motivation_number01 *
  InfoType * InfoImportance) +
  Sex + NeedCog_Mean + 
  (1 | ResponseId)
```

-   A four-way interaction (structure × motivation × info type × info importance)

-   Two control variables: Sex and Need for Cognition

-   A random intercept for `ResponseId` (individual participants)

```{r}
# 2) Build complete-cases dataset for these vars + id
vars_needed <- c("ResponseId", all.vars(form))

dat_full <- gee_long_shared %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

### Run

```{r}
model_mixedCOM <- glmmTMB(form,
               family = compois(),
               data = dat_full
)

summary(model_mixedCOM)
```

#### model checking and diagnotics

```{r}
model_mixedCOM_simres <- simulateResiduals(model_mixedCOM)
plot(model_mixedCOM_simres)
```

Simulated residuals are not uniformly distributed (*p* = .03).

Significant dispersion test (*p* = .04). Model may be over/under dispersed. COM Poisson estimates dispersion.

Outlier test (*p* = .54). No extreme outliers.

Red bands in right plot shows deviations in each quantile. Significant.

Not perfect, but adequate.

#### anova

Model includes interactions -\> use type = "III"

test = "Wald" would not run -\> test = "Chisq"

```{r}
model_mixedCOM_ANOVA <- as.data.frame(car::Anova(model_mixedCOM, type = "III", test.statistic = "Chisq"))

model_mixedCOM_ANOVA
```

#### save

```{r}
saveRDS(model_mixedCOM, 
        file = file.path("../artifacts/model_mixedCOM.rds")
        )
```

### Interpretation

+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| Effect                                      | Estimate | p-value | Interpretation                                                                                                         |
+=============================================+==========+=========+========================================================================================================================+
| **InfoImportancemore**                      | -0.85    | \*\*\*  | “More important” info is associated with less sharing                                                                  |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **Sex1**                                    | -0.20    | \*\*    | Women share less                                                                                                       |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **NeedCog_Mean**                            | +0.21    | \*\*\*  | Higher Need for Cognition → higher sharing                                                                             |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **structure × InfoImportance**              | +0.65    | \*      | Structure effect depends on info importance                                                                            |
|                                             |          |         |                                                                                                                        |
|                                             |          |         | Intergroup settings increase sharing when information is more important.                                               |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **motivation × InfoImportance**             | +0.96    | \*\*\*  | Motivation effect depends on info importance                                                                           |
|                                             |          |         |                                                                                                                        |
|                                             |          |         | Prosocial motivation increases sharing especially when info is more important.                                         |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **InfoType × InfoImportance**               | +0.58    | \*      | Public/private interacts with importance                                                                               |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **structure × motivation × InfoImportance** | -1.31    | \*\*\*  | When info is *more important*, the combined effect of structure × motivation reverses direction (negative synergy)     |
|                                             |          |         |                                                                                                                        |
|                                             |          |         | In important contexts, the prosocial boost is smaller (or reverses) for groups.                                        |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **structure × InfoType × InfoImportance**   | -1.12    | \*\*    | Similar pattern: structural and type effects flip for important info                                                   |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **motivation × InfoType × InfoImportance**  | -0.72    | \*      | Same idea — combined effects are negative when info is important                                                       |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+
| **4-way interaction**                       | +1.34    | \*      | The pattern across all variables shifts depending on all four conditions (most complex interaction)                    |
|                                             |          |         |                                                                                                                        |
|                                             |          |         | This reversal is moderated: in private + important contexts, being intergroup × prosocial does increase sharing again. |
+---------------------------------------------+----------+---------+------------------------------------------------------------------------------------------------------------------------+

The significant three- and four-way interactions suggest:

-   Effects of structure and motivation on sharing depend on both the type of information (public vs. private) and its importance (more vs. less important).

-   The negative 3-way terms and positive 4-way term imply compensatory effects — e.g., under certain conditions (private + important + high motivation), one variable’s influence flips direction.

## Models by Importance

```{r}
#1) Identify the variables in the model
form_limit <- Count ~ (structure_number01 * motivation_number01 * InfoType) +
  Sex + NeedCog_Mean +
  (1 | ResponseId)

# 2) Build complete-cases dataset for these vars + id
vars_needed <- c("ResponseId", all.vars(form_limit))
```

### more

#### data

```{r}
dat_more <- gee_long_shared %>%
  filter(InfoImportance == "more") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

#### model

```{r}
model_mixedCOM_more <- glmmTMB(form_limit,
               family = compois(),
               data = dat_more
)

summary(model_mixedCOM_more)
```

#### anova

```{r}
model_mixedCOM_more_ANOVA <- as.data.frame(
  car::Anova(model_mixedCOM_more, type = "III", test.statistic = "Chisq"))

model_mixedCOM_more_ANOVA
```

#### table

```{r}
dat_more %>%
  group_by(structure_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more %>%
  group_by(motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more %>%
  group_by(InfoType) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

#### figure

```{r}
library(emmeans)

emm <- emmeans(
  model_mixedCOM_more,
  ~ structure_number01 * motivation_number01 * InfoType,
  type = "response"
)

plot_data <- as.data.frame(emm)
```

```{r}
plot_data <- plot_data %>%
  mutate(
    structure_number01 = factor(
      structure_number01,
      levels = c(0,1),
      labels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      motivation_number01,
      levels = c(0,1),
      labels = c("Proself", "Prosocial")
    ),
      InfoType = factor(
      InfoType,
      levels = c("public", "private"),
      labels = c("Common", "Unique")
    )
  )
```

```{r}
names(plot_data)
```

##### fig_info_type_more

```{r}
library(papaja)

fig_info_type <- ggplot(plot_data,
       aes(x = motivation_number01,
           y = response,
           color = InfoType,
           group = InfoType)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    width = .1
  ) +
  facet_wrap(~structure_number01) +
  labs(
    x = "Motivation",
    y = "Predicted count",
    color = "Distribution"
  ) +
  theme_apa()+
  theme(
    text = element_text(size = 30, family = "serif", color = "black"),
    axis.title = element_text(size = 30, face = "bold", color = "black"),
    axis.text = element_text(size = 30, face = "bold", color = "black"),
    
    # ✅ These lines control the TICK MARKS
    axis.ticks = element_line(color = "black", size = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    
    # ✅ These restore AXIS LINES that ticks sit on
    axis.line = element_line(color = "black"),
    
    # ✅ Remove background gridlines (APA prefers a clean look)
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  )

fig_info_type
```

```{r}
ggsave(
  "../figures/fig_info_type.png", 
  plot = fig_info_type, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

##### fig_info_type_more2

```{r}
fig_info_type2 <- ggplot(plot_data,
       aes(x = structure_number01,
           y = response,
           color = motivation_number01,
           group = motivation_number01)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    width = .1
  ) +
  facet_wrap(~InfoType) +
  labs(
    x = "Motivation",
    y = "Predicted count",
    color = "Distribution"
  ) +
  theme_apa()+
  theme(
    text = element_text(size = 30, family = "serif", color = "black"),
    axis.title = element_text(size = 30, face = "bold", color = "black"),
    axis.text = element_text(size = 30, face = "bold", color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    
    # ✅ These lines control the TICK MARKS
    axis.ticks = element_line(color = "black", size = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    
    # ✅ These restore AXIS LINES that ticks sit on
    axis.line = element_line(color = "black"),
    
    # ✅ Remove background gridlines (APA prefers a clean look)
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  )

fig_info_type2
```

```{r}
ggsave(
  "../figures/fig_info_type2.png", 
  plot = fig_info_type2, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

##### fig_bar_more

```{r}
names(plot_data)
```

```{r}
fig_bar_more <- ggplot(
  plot_data,
  aes(x = motivation_number01, y = response, fill = InfoType)
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    alpha = 0.5,
    color = "black", 
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    position = position_dodge(width = 0.8),
    width = 0.25,
    linewidth = 1.2
  ) +
  facet_wrap(~ structure_number01) +
  scale_y_continuous(breaks = seq(0, 3, 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  theme_apa() +
  theme(
  text = element_text(size = 30, family = "serif", color = "black"),
  axis.title = element_text(size = 30, face = "bold", color = "black"),
  axis.text = element_text(size = 30, face = "bold", color = "black"),
  
  # ✅ These lines control the TICK MARKS
  axis.ticks = element_line(color = "black", size = 0.5),
  axis.ticks.length = unit(0.10, "cm"),
  
  # ✅ These restore AXIS LINES that ticks sit on
  axis.line = element_line(color = "black"),
  
  # ✅ Remove background gridlines (APA prefers a clean look)
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.border = element_blank()
  ) +
  labs(
    x = "Motivation",
    y = "Clues Shared"
  ) +
  scale_fill_manual(
    name = "Distribution",
    values = c(
      "Common" = "#0C7BDC",
      "Unique" = "#FFC20A"
    )
  )

fig_bar_more
```

```{r}
ggsave(
  "../figures/fig_bar_more.png", 
  plot = fig_bar_more, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

### less

#### data

```{r}
dat_less <- gee_long_shared %>%
  filter(InfoImportance == "less") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

#### model

```{r}
model_mixedCOM_less <- glmmTMB(form_limit,
               family = compois(),
               data = dat_less
)

summary(model_mixedCOM_less)
```

#### anova

```{r}
model_mixedCOM_less_ANOVA <- as.data.frame(
  car::Anova(model_mixedCOM_less, type = "III", test.statistic = "Chisq"))

model_mixedCOM_less_ANOVA
```

#### table

```{r}
dat_less %>%
  group_by(structure_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less %>%
  group_by(motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less %>%
  group_by(InfoType) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

#### figure

```{r}
emm_less <- emmeans(
  model_mixedCOM_less,
  ~ structure_number01 * motivation_number01 * InfoType,
  type = "response"
)

plot_data_less <- as.data.frame(emm_less)
```

```{r}
plot_data_less <- plot_data_less %>%
  mutate(
    structure_number01 = factor(
      structure_number01,
      levels = c(0,1),
      labels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      motivation_number01,
      levels = c(0,1),
      labels = c("Proself", "Prosocial")
    ),
      InfoType = factor(
      InfoType,
      levels = c("public", "private"),
      labels = c("Common", "Unique")
    )
  )
```

```{r}
fig_info_type_less <- ggplot(plot_data_less,
       aes(x = motivation_number01,
           y = response,
           color = InfoType,
           group = InfoType)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    width = .1
  ) +
  facet_wrap(~structure_number01) +
  labs(
    x = "Motivation",
    y = "Predicted count",
    color = "Distribution"
  ) +
  theme_apa()+
  theme(
    text = element_text(size = 30, family = "serif", color = "black"),
    axis.title = element_text(size = 30, face = "bold", color = "black"),
    axis.text = element_text(size = 30, face = "bold", color = "black"),
    
    # ✅ These lines control the TICK MARKS
    axis.ticks = element_line(color = "black", size = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    
    # ✅ These restore AXIS LINES that ticks sit on
    axis.line = element_line(color = "black"),
    
    # ✅ Remove background gridlines (APA prefers a clean look)
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  )

fig_info_type_less
```

```{r}
ggsave(
  "../figures/fig_info_type_less.png", 
  plot = fig_info_type_less, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

##### fig_bar_less

```{r}
fig_bar_less <- ggplot(
  plot_data_less,
  aes(x = motivation_number01, y = response, fill = InfoType)
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7,
    alpha = 0.5,
    color = "black",   
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    position = position_dodge(width = 0.8),
    width = 0.25,
    linewidth = 1.2
  ) +
  facet_wrap(~ structure_number01) +
  scale_y_continuous(breaks = seq(0, 3, 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  theme_apa() +
  theme(
  text = element_text(size = 30, family = "serif", color = "black"),
  axis.title = element_text(size = 30, face = "bold", color = "black"),
  axis.text = element_text(size = 30, face = "bold", color = "black"),
  
  # ✅ These lines control the TICK MARKS
  axis.ticks = element_line(color = "black", size = 0.5),
  axis.ticks.length = unit(0.10, "cm"),
  
  # ✅ These restore AXIS LINES that ticks sit on
  axis.line = element_line(color = "black"),
  
  # ✅ Remove background gridlines (APA prefers a clean look)
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.border = element_blank()
  ) +
  labs(
    x = "Motivation",
    y = "Clues Shared"
  ) +
  scale_fill_manual(
    name = "Distribution",
    values = c(
      "Common" = "#0C7BDC",
      "Unique" = "#FFC20A"
    )
  )

fig_bar_less
```

```{r}
ggsave(
  "../figures/fig_bar_less.png", 
  plot = fig_bar_less, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

## Models by Type and Importance

### Setup

```{r}
#1) Identify the variables in the model
form_limit <- Count ~ (structure_number01 * motivation_number01) +
  Sex + NeedCog_Mean + 
  (1 | ResponseId)

# 2) Build complete-cases dataset for these vars + id
vars_needed <- c("ResponseId", all.vars(form_limit))
```

#### InfoType, public private

```{r}
glimpse(dat_full$InfoType)
# 1 = public
# 2 = private
```

#### InfoImport, less more

```{r}
glimpse(dat_full$InfoImportance)
# 1 = less
# 2 = more
```

#### structure

```{r}
filtered_data <- readRDS("../artifacts/filtered_data.rds")
```

```{r}
head(filtered_data[c("structure", "structure_number01")])
# 0 = interindividual
# 1 = intergroup
```

```{r}
# structure(filtered_data$structure)
```

#### motivation

```{r}
head(filtered_data[c("motivation", "motivation_number01")])
```

```{r}
glimpse(dat_full$motivation_number01)
# 0 = proself
# 1 = prosocial
```

#### levels of variables

**structure**

0 = interindividual

1 = intergroup

**motivation**

0 = proself

1 = prosocial

**type**

public

private

**importance**

less

more

### High/More & Private/Unique

#### data

```{r}
dat_more_private <- gee_long_shared %>%
  filter(InfoImportance == "more" & InfoType == "private") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

#### model

```{r}
model_mixedCOM_mp <- glmmTMB(form_limit,
               family = compois(),
               data = dat_more_private
)

summary(model_mixedCOM_mp)
```

#### anova

```{r}
model_mixedCOM_mp_ANOVA <- as.data.frame(car::Anova(model_mixedCOM_mp, type = "III", test.statistic = "Chisq"))

model_mixedCOM_mp_ANOVA
```

#### emeans

```{r}
# emmeans(model_mixedCOM_mp, poly ~ )
```

#### save

```{r}
saveRDS(model_mixedCOM_mp,  
        file = file.path("../artifacts/model_mixedCOM_mp.rds")
        )
```

#### table

```{r}
dat_more_private %>%
  group_by(structure_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more_private %>%
  group_by(motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more_private %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
desc_by_cell_input(dat_more_private, group_vars = c("structure_number01", "motivation_number01"), var = "Count")
```

#### figure

```{r}
interaction_data_more_private <- dat_more_private %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE),
    n = n(),
    se = sd_value / sqrt(n),
    .groups = "drop"
  )
```

```{r}
# interaction_data <- interaction_data %>%
#   mutate(
#     structure_number01 = factor(
#       structure_number01,
#       levels = c(0,1),
#       labels = c("Interindividual", "Intergroup")
#     ),
#     motivation_number01 = factor(
#       motivation_number01,
#       levels = c(0,1),
#       labels = c("Proself", "Prosocial")
#     )
#   )

interaction_data_more_private <- interaction_data_more_private %>%
  mutate(
    structure_number01 = factor(
      as.numeric(unclass(structure_number01)),
      levels = c(0, 1),
      labels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      as.numeric(unclass(motivation_number01)),
      levels = c(0, 1),
      labels = c("Proself", "Prosocial")
    )
  )
```

```{r}
# fig_more_private <- ggplot(interaction_data_more_private,
#        aes(x = structure_number01,
#            y = mean_value,
#            color = motivation_number01,
#            group = motivation_number01)) +
#   geom_point(size = 3) +
#   geom_line() +
#   geom_errorbar(
#     aes(ymin = mean_value - se, ymax = mean_value + se),
#     width = .1
#   ) +
#   labs(
#     x = "Structure",
#     y = "Mean number of clues shared",
#     color = "Motivation"
#   ) +
#   theme_apa()+
#   theme(
#     text = element_text(size = 30, family = "serif", color = "black"),
#     axis.title = element_text(size = 30, face = "bold", color = "black"),
#     axis.text = element_text(size = 30, face = "bold", color = "black"),
#     
#     # ✅ These lines control the TICK MARKS
#     axis.ticks = element_line(color = "black", size = 0.5),
#     axis.ticks.length = unit(0.10, "cm"),
#     
#     # ✅ These restore AXIS LINES that ticks sit on
#     axis.line = element_line(color = "black"),
#     
#     # ✅ Remove background gridlines (APA prefers a clean look)
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.border = element_blank()
#   )
# 
# fig_more_private
```

```{r}
# ggsave(
#   "../figures/fig_more_private.png", 
#   plot = fig_more_private, 
#   width = 6.5,   height = 4.5, 
#   units = "in",
#   scale = 2, 
#   dpi = 72
#   # device = Cairo::CairoPNG
#   )
```

##### fig_bar_more_private2

```{r}
# pd <- position_dodge(width = 0.8)
# 
# fig_bar_more_private <- ggplot(
#   interaction_data_more_private,
#   aes(
#     x = structure_number01,
#     y = mean_value,
#     fill = motivation_number01
#   )
# ) +
#   geom_col(
#     position = pd,
#     width = 0.7,
#     alpha = 0.5
#   ) +
#   geom_errorbar(
#     aes(ymin = mean_value - se, ymax = mean_value + se),
#     position = pd,
#     width = 0.25,
#     linewidth = 1.2
#   ) +
#   labs(
#     x = "Structure",
#     y = "Mean number of clues shared",
#     fill = "Motivation"
#   ) +
#   scale_y_continuous(breaks = seq(0, 3, 1)) +
#   coord_cartesian(ylim = c(0, 3)) +
#   theme_apa() +
#   theme(
#     text = element_text(size = 30, family = "serif", color = "black"),
#     axis.title = element_text(size = 30, face = "bold", color = "black"),
#     axis.text = element_text(size = 30, face = "bold", color = "black"),
#     axis.ticks = element_line(color = "black", linewidth = 0.5),
#     axis.ticks.length = unit(0.10, "cm"),
#     axis.line = element_line(color = "black"),
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.border = element_blank()
#   )
# 
# fig_bar_more_private
```

```{r}
# ggsave(
#   "../figures/fig_bar_more_private.png", 
#   plot = fig_bar_more_private, 
#   width = 6.5,   height = 4.5, 
#   units = "in",
#   scale = 2, 
#   dpi = 72
#   # device = Cairo::CairoPNG
#   )
```

```{r}
fig_bar_more_private2 <- ggplot(
  interaction_data_more_private,
  aes(x = motivation_number01, y = mean_value)
) +
  geom_col(
    fill = "#FFC20A",
    width = 0.7,
    alpha = 0.5,
    color = "black",   
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(ymin = mean_value - se, ymax = mean_value + se),
    width = 0.25,
    linewidth = 1.2
  ) +
  facet_wrap(~ structure_number01) +
  scale_y_continuous(breaks = seq(0, 3, 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(
    x = "Motivation",
    y = "Clues Shared"
  ) +
  theme_apa() +
  theme(
    text = element_text(size = 30, family = "serif", color = "black"),
    axis.title = element_text(size = 30, face = "bold", color = "black"),
    axis.text = element_text(size = 30, face = "bold", color = "black"),
    axis.ticks = element_line(color = "black", linewidth = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    legend.position = "none"
  )

fig_bar_more_private2
```

```{r}
ggsave(
  "../figures/fig_bar_more_private2.png", 
  plot = fig_bar_more_private2, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

### High/More & Common/Public

#### data

```{r}
dat_more_public <- gee_long_shared %>%
  filter(InfoImportance == "more" & InfoType == "public") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

#### model

```{r}
model_mixedCOM_mc <- glmmTMB(form_limit,
               family = compois(),
               data = dat_more_public
)

summary(model_mixedCOM_mc)
```

#### anova

```{r}
model_mixedCOM_mc_ANOVA <- as.data.frame(car::Anova(model_mixedCOM_mc, type = "III", test.statistic = "Chisq"))

model_mixedCOM_mc_ANOVA
```

#### save

```{r}
saveRDS(model_mixedCOM_mc,  
        file = file.path("../artifacts/model_mixedCOM_mc.rds")
        )
```

#### table

```{r}
dat_more_public %>%
  group_by(structure_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more_public %>%
  group_by(motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_more_public %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
desc_by_cell_input(dat_more_public, group_vars = c("structure_number01", "motivation_number01"), var = "Count")
```

#### figure

```{r}
interaction_data_more_public <- dat_more_public %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE),
    n = n(),
    se = sd_value / sqrt(n),
    .groups = "drop"
  )
```

```{r}
interaction_data_more_public <- interaction_data_more_public %>%
  mutate(
    structure_number01 = factor(
      as.numeric(unclass(structure_number01)),
      levels = c(0, 1),
      labels = c("Interindividual", "Intergroup")
    ),
    motivation_number01 = factor(
      as.numeric(unclass(motivation_number01)),
      levels = c(0, 1),
      labels = c("Proself", "Prosocial")
    )
  )
```

##### fit_more_public

```{r}
# fit_more_public <- ggplot(interaction_data_more_public,
#        aes(x = structure_number01,
#            y = mean_value,
#            color = motivation_number01,
#            group = motivation_number01)) +
#   geom_point(size = 3) +
#   geom_line() +
#   geom_errorbar(
#     aes(ymin = mean_value - se, ymax = mean_value + se),
#     width = .1
#   ) +
#   labs(
#     x = "Structure",
#     y = "Mean number of clues shared",
#     color = "Motivation"
#   ) +
#   theme_apa()+
#   theme(
#     text = element_text(size = 30, family = "serif", color = "black"),
#     axis.title = element_text(size = 30, face = "bold", color = "black"),
#     axis.text = element_text(size = 30, face = "bold", color = "black"),
#     
#     # ✅ These lines control the TICK MARKS
#     axis.ticks = element_line(color = "black", size = 0.5),
#     axis.ticks.length = unit(0.10, "cm"),
#     
#     # ✅ These restore AXIS LINES that ticks sit on
#     axis.line = element_line(color = "black"),
#     
#     # ✅ Remove background gridlines (APA prefers a clean look)
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.border = element_blank()
#   )
# 
# fit_more_public
```

```{r}
# ggsave(
#   "../figures/fit_more_public.png", 
#   plot = fit_more_public, 
#   width = 6.5,   height = 4.5, 
#   units = "in",
#   scale = 2, 
#   dpi = 72
#   # device = Cairo::CairoPNG
#   )
```

##### fig_bar_more_public

```{r}
fig_bar_more_public <- ggplot(
  interaction_data_more_public,
  aes(x = motivation_number01, y = mean_value)
) +
  geom_col(
    fill = "#0C7BDC",
    width = 0.7,
    alpha = 0.5,
    color = "black",   
    linewidth = 0.2
  ) +
  geom_errorbar(
    aes(ymin = mean_value - se, ymax = mean_value + se),
    width = 0.25,
    linewidth = 1.2
  ) +
  facet_wrap(~ structure_number01) +
  scale_y_continuous(breaks = seq(0, 3, 1)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(
    x = "Motivation",
    y = "Clues Shared"
  ) +
  theme_apa() +
  theme(
    text = element_text(size = 30, family = "serif", color = "black"),
    axis.title = element_text(size = 30, face = "bold", color = "black"),
    axis.text = element_text(size = 30, face = "bold", color = "black"),
    axis.ticks = element_line(color = "black", linewidth = 0.5),
    axis.ticks.length = unit(0.10, "cm"),
    axis.line = element_line(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    legend.position = "none"
  )

fig_bar_more_public
```

```{r}
ggsave(
  "../figures/fig_bar_more_public.png", 
  plot = fig_bar_more_public, 
  width = 6.5,   height = 4.5, 
  units = "in",
  scale = 2, 
  dpi = 72
  # device = Cairo::CairoPNG
  )
```

### Low/Less & Private/Unique

#### data

```{r}
dat_less_private <- gee_long_shared %>%
  filter(InfoImportance == "less" & InfoType == "private") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

#### model

```{r}
model_mixedCOM_lp <- glmmTMB(form_limit,
               family = compois(),
               data = dat_less_private
)

summary(model_mixedCOM_lp)
```

#### anova

```{r}
model_mixedCOM_lp_ANOVA <- as.data.frame(car::Anova(model_mixedCOM_lp, type = "III", test.statistic = "Chisq"))

model_mixedCOM_lp_ANOVA
```

#### save

```{r}
saveRDS(model_mixedCOM_lp,  
        file = file.path("../artifacts/model_mixedCOM_lp.rds")
        )
```

#### table

```{r}
dat_less_private %>%
  group_by(structure_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less_private %>%
  group_by(motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less_private %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
desc_by_cell_input(dat_less_private, group_vars = c("structure_number01", "motivation_number01"), var = "Count")
```

### Low/Less & Common/Public

#### data

```{r}
dat_less_public <- gee_long_shared %>%
  filter(InfoImportance == "less" & InfoType == "public") %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

#### model

```{r}
model_mixedCOM_lc <- glmmTMB(form_limit,
               family = compois(),
               data = dat_less_public
)

summary(model_mixedCOM_lc)
```

#### anova

```{r}
model_mixedCOM_lc_ANOVA <- as.data.frame(car::Anova(model_mixedCOM_lc, type = "III", test.statistic = "Chisq"))

model_mixedCOM_lp_ANOVA
```

#### save

```{r}
saveRDS(model_mixedCOM_lc,  
        file = file.path("../artifacts/model_mixedCOM_lc.rds")
        )
```

#### table

```{r}
dat_less_public %>%
  group_by(structure_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less_public %>%
  group_by(motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
dat_less_public %>%
  group_by(structure_number01, motivation_number01) %>%
  summarise(
    mean_value = mean(Count, na.rm = TRUE),
    sd_value = sd(Count, na.rm = TRUE)
  )
```

```{r}
desc_by_cell_input(dat_less_public, group_vars = c("structure_number01", "motivation_number01"), var = "Count")
```

## ---End---

```{r}
save.image(file = "../artifacts/COMPoisson.RData")
# End of section
```

## Interpretation

Structure: \# 0 = interindividual \# 1 = intergroup

Motivation: \# 0 = proself \# 1 = prosocial

### More Private (`dat_more_private`)

| Effect              | Est   | p   |
|---------------------|-------|-----|
| motivation_number01 | +0.51 | \*  |
| Sex1                | -0.35 | \*  |

➡️ In the *more private* condition, motivation increases counts, and women have lower counts.

### More Public (`dat_more_public`)

| Effect                 | Est   | p      |
|------------------------|-------|--------|
| structure_number01     | +0.63 | \*\*   |
| motivation_number01    | +0.98 | \*\*\* |
| structure × motivation | -1.04 | \*\*\* |
| Sex1                   | -0.45 | \*\*   |
| NeedCog_Mean           | +0.31 | \*\*   |

In the *more public* condition:

-   Both structure and motivation increase counts individually.

-   But together, their interaction is negative, suggesting diminishing returns (when both are high, the effect drops).

-   Again, Need for Cognition → higher counts; Sex1 (women) → fewer counts.

### Less Private (`dat_less_private`)

| Effect              | Est   | p    |
|---------------------|-------|------|
| motivation_number01 | +0.29 | \*   |
| NeedCog_Mean        | +0.27 | \*\* |

In *less private* settings:

-   Motivation alone drives higher counts.

-   Need for Cognition remains a consistent positive predictor.

### Less Public (`dat_less_public`)

| Effect       | Est   | p   |
|--------------|-------|-----|
| NeedCog_Mean | +0.19 | \*  |

➡️ In *less public* settings:

-   Only **Need for Cognition** predicts higher counts.

-   Motivation and structure no longer matter here.

### Table

| Condition | Key Drivers | Pattern |
|----|----|----|
| **More Private** | Motivation (+), Sex (−) | People high in motivation share/do more in private contexts; women share less. |
| **More Public** | Structure (+), Motivation (+), Need for Cognition (+), Sex (−); interaction (−) | Structure and motivation both help, but if both are high, effect drops — possibly due to strategic restraint in public settings. |
| **Less Private** | Motivation (+), Need for Cognition (+) | Motivation and cognition facilitate more behavior. |
| **Less Public** | Need for Cognition (+) | Only thoughtful individuals show higher counts. |

-   Importance, motivation, and Need for Cognition are consistently impactful.
-   Interactions show that context (public/private, importance) changes how motivation and structure matter.
-   Sex differences appear primarily in the “more private” and “more public” contexts.
-   Overdispersion justifies the COM-Poisson model choice.
-   Participant-level variability is negligible.

## Summary

### Full model

| Interaction term | Estimate | p | Interpretation |
|----|----|----|----|
| structure × InfoImportance | +0.65 | \* | Structure increases count **when info is more important**. |
| motivation × InfoImportance | +0.96 | \*\*\* | Motivation increases count **when info is more important**. |
| structure × motivation × InfoImportance | −1.31 | \*\*\* | The combined structure+motivation effect reverses when info is more important. |
| structure × motivation × InfoType × InfoImportance | +1.34 | \* | In the specific context of **private + important** information, structure and motivation jointly enhance counts. |

### Subset models

+------------------+------------------------+-------------------------+-------------------------+-------------------------------------------------------------------------------------------------------------------------------------------+
| Condition        | structure              | motivation              | interaction             | takeaway                                                                                                                                  |
+==================+========================+=========================+=========================+===========================================================================================================================================+
| **More Private** | —                      | **positive, p \< .05**  | ns                      | Motivation drives higher counts in private/important contexts. Structure doesn’t matter much.                                             |
|                  |                        |                         |                         |                                                                                                                                           |
|                  |                        |                         |                         | Prosocial participants share more when information is important and private, regardless of structure.                                     |
+------------------+------------------------+-------------------------+-------------------------+-------------------------------------------------------------------------------------------------------------------------------------------+
| **More Public**  | **positive, p \< .01** | **positive, p \< .001** | **negative, p \< .001** | Intergroup and prosocial each promote sharing, but together they reduce it — prosocial motives may be tempered in visible group contexts. |
+------------------+------------------------+-------------------------+-------------------------+-------------------------------------------------------------------------------------------------------------------------------------------+
| **Less Private** | —                      | **positive, p \< .05**  | ns                      | Same pattern: prosocial → higher counts.                                                                                                  |
+------------------+------------------------+-------------------------+-------------------------+-------------------------------------------------------------------------------------------------------------------------------------------+
| **Less Public**  | —                      | —                       | ns                      | Neither manipulation matters when info is less important and public.                                                                      |
+------------------+------------------------+-------------------------+-------------------------+-------------------------------------------------------------------------------------------------------------------------------------------+

### Story

| Manipulation | Summary pattern | Interpretation |
|----|----|----|
| **Motivation** | Consistent positive effect — especially in *private* or *important* contexts | Highly motivated individuals engage more, particularly when stakes or importance are high. |
| **Structure** | Helps mainly in *public* settings, but not in private ones | Structured environments seem to facilitate sharing/action when visibility is higher. |
| **Interaction (Structure × Motivation)** | Negative in *more public* condition | When both structure and motivation are high, participants may regulate their behavior — perhaps avoiding appearing overly dominant or competitive. |

-   **Motivation** reliably predicts higher sharing (strongest and most consistent effect).

-   **Structure** matters mostly when the information is **public** or **important**.

-   When interindividual × prosocial, they act more freely — higher sharing without fear of group reputation loss.

-   This supports the idea that social visibility moderates how prosocial motivation is expressed in groups, consistent with strategic prosociality or reputation management frameworks.
