---
title: "05_01_01_PowerAnalysis"
format: html
---

# Power Analysis

Possible packages:

~~**`powerlmm`**  - longitudinal data, NA~~

`pwr` - basic power analysis, but includes [Wald test](https://cran.r-project.org/web/packages/pwrss/vignettes/examples.html#7_Regression:_Poisson_(Wald%E2%80%99s_Z-Test)), might work if no manipulations

`simr` - mixed-effects general linear models \<----- best option due to complex model

## Study 1

```{r}
gee_long_shared <- readRDS("../artifacts/gee_long_shared.rds")
codebook <- readRDS("../artifacts/codebook.rds")
library(glmmTMB)
source("../_common.R")
```

```{r}
form <- Count ~ (structure_number01 * motivation_number01 *
  InfoType * InfoImportance) +
  Sex + NeedCog_Mean + 
  (1 | ResponseId)
```

```{r}
vars_needed <- c("ResponseId", all.vars(form))

dat_full <- gee_long_shared %>%
  mutate(across(where(is.character), factor)) %>%
  dplyr::select(all_of(vars_needed)) %>%
  filter(complete.cases(.)) %>%
  droplevels()
```

### full model

```{r}
form <- Count ~ (structure_number01 * motivation_number01 *
  InfoType * InfoImportance) +
  Sex + NeedCog_Mean + 
  (1 | ResponseId)
```

```{r}
fit <- glmmTMB(form,
  data = dat_full,
  family = compois(link = "log")
)
```

```{r}
# summary(fit)
```

### null model

```{r}
form_null <- Count ~ Sex + NeedCog_Mean + (1 | ResponseId)

fit_null <- glmmTMB(
  form_null,
  data = dat_full,
  family = compois(link = "log")
)
```

### simulate global

```{r}
one_run_global <- function(fit_full, fit_null) {
  dat_sim <- model.frame(fit_full)

  # Step 2: simulate a new outcome vector under the full model
  dat_sim$Count <- as.numeric(simulate(fit_full, nsim = 1)[[1]])

  # Step 3: refit models to the simulated data
  full_refit <- try(update(fit_full, data = dat_sim), silent = TRUE)
  if (inherits(full_refit, "try-error")) return(NA)

  null_refit <- try(update(fit_null, data = dat_sim), silent = TRUE)
  if (inherits(null_refit, "try-error")) return(NA)

  # Global LRT: does full beat null?
  p <- anova(null_refit, full_refit)$`Pr(>Chisq)`[2]
  isTRUE(p < 0.05)
}

set.seed(1)
one_run_global(fit, fit_null)

```

```{r}
# set.seed(1)
# nsim <- 100    # number of simulations to run
# 
# res <- sapply(seq_len(nsim), function(i) {
#   if (i %% 5 == 0) message("Simulation ", i, "/", nsim)
#   one_run_global(fit, fit_null)
# })
# 
# power_est <- mean(res, na.rm = TRUE)
# fail_rate <- mean(is.na(res))
# 
# power_est
# fail_rate
```

### simulate 4 way

```{r}
one_run_term <- function(fit_full, drop_term) {
  dat_sim <- model.frame(fit_full)
  dat_sim$Count <- as.numeric(simulate(fit_full, nsim = 1)[[1]])

  full_refit <- try(update(fit_full, data = dat_sim), silent = TRUE)
  if (inherits(full_refit, "try-error")) return(NA)

  red_refit <- try(
    update(full_refit, as.formula(paste(". ~ . -", drop_term))),
    silent = TRUE
  )
  if (inherits(red_refit, "try-error")) return(NA)

  p <- anova(red_refit, full_refit)$`Pr(>Chisq)`[2]
  isTRUE(p < 0.05)
}
```

```{r}
set.seed(1)
nsim <- 5

res_4way <- sapply(seq_len(nsim), function(i) {
  if (i %% 5 == 0) message("Simulation ", i, "/", nsim)
  one_run_term(
    fit,
    "structure_number01:motivation_number01:InfoType:InfoImportance"
  )
})

mean(res_4way, na.rm = TRUE)
mean(is.na(res_4way))
```

```{r}
# simulate(fit, nsim = 1)
```

## Study 2

```{r}
library(simr)
library(lme4)

# 1. Create a dummy data frame representing your factorial design
# Replace 'n_subj' with a starting guess (e.g., 60)
n_subj <- 240 
subj_ids <- 1:n_subj
structure <- c("S1", "S2", "S3")
motivation <- c("M1", "M2")
info_type <- c("T1", "T2")
importance <- c("High", "Low")
items <- 1:5

df <- expand.grid(ResponseId=subj_ids, structure=structure, motivation=motivation, 
                  info_type=info_type, importance=importance, item=items)

# 2. Define the Fixed Effects (The Intercept and the 4-way interaction)
# We set all other effects to 0 for a conservative test of the 4-way term
fixed <- c(0.18, rep(0, 22), 1.34) # 0.18 is intercept, 1.34 is the last interaction term

# 3. Define Random Effects (Subject variance)
# Using 0.1 as a conservative estimate since your pilot was nearly 0
rand <- 0.1 

# 4. Create the model object
model <- makeGlmer(y ~ structure*motivation*info_type*importance + (1|ResponseId), 
                   family="poisson", fixef=fixed, VarCorr=rand, data=df)

# 5. Run the power analysis
power_sim <- powerSim(model, fixed("structure:motivation:info_type:importance", "lr"), nsim=100)
print(power_sim)
```
